---
title: "plot_errors"
author: "Doudou Carol Cao"
date: "2023-06-14"
output: html_document
---

# 8. Plot
## 8.1. Set the parameter for indicative lines and common colour scale for each graph
```{r}
# parameter for indicative lines
simulated_n <- c (30, 50, 100, 150)
simulated_c <- c (0.25, 0.5, 0.75)

# Find the common color scale limits for different sets of plots (mean, median, 75 percentile, and the number as well as proportion of large errors)
## BI
color_scale_mean_bi <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_bi$mean_abs_error), max(results_df_bi$mean_abs_error)))
color_scale_median_bi <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_bi$median_abs_error), max(results_df_bi$median_abs_error)))
color_scale_percentile_75_bi <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_bi$percentile_75), max(results_df_bi$percentile_75)))
color_scale_no_large_error_bi <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_bi$abs_error_count), max(results_df_bi$abs_error_count)))
## CI
color_scale_mean_ci <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_ci$mean_abs_error), max(results_df_ci$mean_abs_error)))
color_scale_median_ci <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_ci$median_abs_error), max(results_df_ci$median_abs_error)))
color_scale_percentile_75_ci <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_ci$percentile_75), max(results_df_ci$percentile_75)))
color_scale_no_large_error_ci <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_ci$abs_error_count), max(results_df_ci$abs_error_count)))
```

## 8.2. Plot-BI
### 8.2.1.Variation = 0.01
#### 8.2.1.1. Mean error ~ sample size + commingling
```{r}
plot01 <- ggplot(results_df_bi[results_df_bi$v == 0.01, ], aes(x = n, y = c, fill = mean_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  color_scale_mean_bi +
  xlab('Sample Size') +
  ylab('Commingling degree') +
  labs(fill = "Mean Errors\
(sd.cBI = 0.01)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot01
```

#### 8.2.1.2. Median absolute error ~ sample size + commingling
```{r}
plot02 <- ggplot(results_df_bi[results_df_bi$v == 0.01, ], aes(x = n, y = c, fill = median_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_median_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Median Errors\
(sd.cBI = 0.01)
") +
  coord_cartesian(expand = FALSE) +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))


# Print
plot02
```

#### 8.2.1.3. Error 75%  ~ sample size + commingling
```{r}
plot03 <- ggplot(results_df_bi[results_df_bi$v == 0.01, ], aes(x = n, y = c, fill = percentile_75)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_percentile_75_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "75th Percentile\
(sd.cBI = 0.01)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))


# Print
plot03
```

#### 8.2.1.4.  Large error count ~ sample size + commingling
```{r}
plot04 <- ggplot(results_df_bi[results_df_bi$v == 0.01, ], aes(x = n, y = c, fill = abs_error_count)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_no_large_error_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "The Number of\
Large Errors\
(sd.cBI = 0.02)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot04
```

#### 8.2.1.5.  Proportion of large error ~ sample size + commingling
```{r}

# Filter the data for v = 0.01
filtered_biv_0.01 <- subset(results_df_bi, v == 0.01)

# Create the categorical variable for prop_large_error ranges
filtered_biv_0.01$prop_large_error_range_biv_0.01 <- cut(filtered_biv_0.01$prop_large_error, 
                                            breaks = c(0, 0.01, 0.05, 0.1, 0.2, 1),
                                            labels = c("< 1%", "1% - 5%", "5% - 10%", "10% - 20%", "> 20%"),
                                            include.lowest = TRUE)

library(RColorBrewer)

# Define the number of colors in the color scheme
num_colors <- 5

# Generate a color palette from red to light blue
color_palette <- brewer.pal(num_colors, "RdYlBu")

# Reverse the color palette to start from red
color_palette <- rev(color_palette)

plot05 <- ggplot(filtered_biv_0.01, aes(x = n, y = c, fill = prop_large_error_range_biv_0.01)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  scale_fill_manual(values = color_palette) +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "the Proportion of \nLarge Errors\n(sd.cBI = 0.01)
       ") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print the plot
print(plot05)
```

### 8.2.2. Variation = 0.02
#### 8.2.2.1. Mean error ~ sample size + commingling
```{r}
plot06 <- ggplot(results_df_bi[results_df_bi$v == 0.02, ], aes(x = n, y = c, fill = mean_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  color_scale_mean_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Mean Errors\
(sd.cBI = 0.02)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot06
```

#### 8.2.2.2. Median absolute error ~ sample size + commingling
```{r}
plot07 <- ggplot(results_df_bi[results_df_bi$v == 0.02, ], aes(x = n, y = c, fill = median_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_median_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Median Errors\
(sd.cBI = 0.02)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot07
```

#### 8.2.2.3. Error 75%  ~ sample size + commingling
```{r}
plot08 <- ggplot(results_df_bi[results_df_bi$v == 0.02, ], aes(x = n, y = c, fill = percentile_75)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_percentile_75_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "75th Percentile\
(sd.cBI = 0.02)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot08     
```

#### 8.2.2.4. Large error count ~ sample size + commingling
```{r}
plot09 <- ggplot(results_df_bi[results_df_bi$v == 0.02, ], aes(x = n, y = c, fill = abs_error_count)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_no_large_error_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "The Number of\
Large Error\
(sd.cBI = 0.02)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot09
```

#### 8.2.2.5. Proportion of large error ~ sample size + commingling
```{r}
# Filter the data for v = 0.01
filtered_biv_0.02 <- subset(results_df_bi, v == 0.02)

# Create the categorical variable for prop_large_error ranges
filtered_biv_0.02$prop_large_error_range_biv_0.02 <- cut(filtered_biv_0.02$prop_large_error, 
                                            breaks = c(0, 0.01, 0.05, 0.1, 0.2, 1),
                                            labels = c("< 1%", "1% - 5%", "5% - 10%", "10% - 20%", "> 20%"),
                                            include.lowest = TRUE)

  
plot010 <- ggplot(filtered_biv_0.02, aes(x = n, y = c, fill = prop_large_error_range_biv_0.02)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  scale_fill_manual(values = color_palette) +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "The Proportion of\
Large Errors \
(sd.cBI = 0.02)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot010
```

### 8.2.1. Variation = 0.08/0.05(for the propotion)
#### 8.2.3.1. Mean error ~ sample size + commingling
```{r}
plot011 <- ggplot(results_df_bi[results_df_bi$v == 0.08, ], aes(x = n, y = c, fill = mean_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  color_scale_mean_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Mean Errors\
(sd.cBI = 0.08)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot011
```

#### 8.2.3.2. Median absolute error ~ sample size + commingling
```{r}
plot012 <- ggplot(results_df_bi[results_df_bi$v == 0.08, ], aes(x = n, y = c, fill = median_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_median_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Median Errors\
(sd.cBI = 0.08)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot012
```

#### 8.2.3.3. Error 75%  ~ sample size + commingling
```{r}
plot013 <- ggplot(results_df_bi[results_df_bi$v == 0.08, ], aes(x = n, y = c, fill = percentile_75)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_percentile_75_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "75th Percentile\
(sd.cBI = 0.08)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot013      
```

#### 8.2.3.4. Large error count ~ sample size + commingling
```{r}
plot014 <- ggplot(results_df_bi[results_df_bi$v == 0.08, ], aes(x = n, y = c, fill = abs_error_count)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_no_large_error_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "The Number of\
Large Error\
(sd.cBI = 0.08)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot014

```

#### 8.2.3.5. Proportion of large error ~ sample size + commingling
```{r}
# Filter the data for v = 0.05
filtered_biv_0.05 <- subset(results_df_bi, v == 0.05)

# Create the categorical variable for prop_large_error ranges
filtered_biv_0.05$prop_large_error_range_biv_0.05 <- cut(filtered_biv_0.05$prop_large_error, 
                                            breaks = c(0, 0.01, 0.05, 0.1, 0.2, 1),
                                            labels = c("< 1%", "1% - 5%", "5% - 10%", "10% - 20%", "> 20%"),
                                            include.lowest = TRUE)

  
  plot015 <- ggplot(filtered_biv_0.05, aes(x = n, y = c, fill = prop_large_error_range_biv_0.05)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  scale_fill_manual(values = color_palette) +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "The Proportion of\
Large Errors \
(sd.cBI = 0.05)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot015
```

#### 8.2.3.6. Proportion of large error ~ sample size + commingling
```{r}
# Filter the data for v = 0.08
filtered_biv_0.08 <- subset(results_df_bi, v == 0.08)

# Create the categorical variable for prop_large_error ranges
filtered_biv_0.08$prop_large_error_range_biv_0.08 <- cut(filtered_biv_0.08$prop_large_error, 
                                            breaks = c(0, 0.01, 0.05, 0.1, 0.2, 1),
                                            labels = c("< 1%", "1% - 5%", "5% - 10%", "10% - 20%", "> 20%"),
                                            include.lowest = TRUE)

  
  plot016 <- ggplot(filtered_biv_0.08, aes(x = n, y = c, fill = prop_large_error_range_biv_0.08)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  scale_fill_manual(values = color_palette) +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "The Proportion of\
Large Errors\
(sd.cBI = 0.08)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot016
```

## 8.3. Plot CI
### 8.3.1. Variation = 0.01
#### 8.3.1.1. Mean error ~ sample size + commingling
```{r}

plot1 <- ggplot(results_df_ci[results_df_ci$v == 0.01, ], aes(x = n, y = c, fill = mean_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  color_scale_mean_ci +
  xlab('Sample Size') +
  ylab('Commingling degree') +
  labs(fill = "Mean Errors\
(sd.cBI = 0.01)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot1

```

#### 8.3.1.2. Median absolute error ~ sample size + commingling
```{r}
plot2 <- ggplot(results_df_ci[results_df_ci$v == 0.01, ], aes(x = n, y = c, fill = median_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_median_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Median Errors\
(sd.cCI = 0.01)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot2
```

#### 8.3.1.3. Error 75%  ~ sample size + commingling
```{r}
plot3 <- ggplot(results_df_ci[results_df_ci$v == 0.01, ], aes(x = n, y = c, fill = percentile_75)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_percentile_75_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "75th Percentile 
(sd.cCIgroup = 0.01)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot3
```

#### 8.3.1.4. Large error count ~ sample size + commingling
```{r}
plot4 <- ggplot(results_df_ci[results_df_ci$v == 0.01, ], aes(x = n, y = c, fill = abs_error_count)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_no_large_error_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "The Number of\
Large Errors\
(sd.cCI = 0.01)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot4
```

#### 8.3.1.5. Proportion of large error ~ sample size + commingling
```{r}
# Filter the data for v = 0.01
filtered_civ_0.01 <- subset(results_df_ci, v == 0.01)

# Create the categorical variable for prop_large_error ranges
filtered_civ_0.01$prop_large_error_range_civ_0.01 <- cut(filtered_civ_0.01$prop_large_error, 
                                            breaks = c(0, 0.01, 0.05, 0.1, 0.2, 1),
                                            labels = c("< 1%", "1% - 5%", "5% - 10%", "10% - 20%", "> 20%"),
                                            include.lowest = TRUE)

  
plot5 <- ggplot(filtered_civ_0.01, aes(x = n, y = c, fill = prop_large_error_range_civ_0.01)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  scale_fill_manual(values = color_palette) +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Proportion of\
Large Errors\
(sd.cCI = 0.01)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot5
```

### 8.3.2. Variation = 0.02
#### 8.3.2.1. Mean error ~ sample size + commingling
```{r}

plot6 <- ggplot(results_df_ci[results_df_ci$v == 0.02, ], aes(x = n, y = c, fill = mean_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  color_scale_mean_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Mean Errors\
(sd.cCI = 0.02)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot6
```

#### 8.3.2.2. Median absolute error ~ sample size + commingling
```{r}
plot7 <- ggplot(results_df_ci[results_df_ci$v == 0.02, ], aes(x = n, y = c, fill = median_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_median_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Median Errors\
(sd.cCI = 0.02)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot7
```

#### 8.3.2.3. Error 75%  ~ sample size + commingling
```{r}
plot8 <- ggplot(results_df_ci[results_df_ci$v == 0.02, ], aes(x = n, y = c, fill = percentile_75)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_percentile_75_ci+
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "75th Percentile\
(sd.cCI = 0.02)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot8
```

#### 8.3.2.4. Large error count ~ sample size + commingling
```{r}
plot9 <- ggplot(results_df_ci[results_df_ci$v == 0.02, ], aes(x = n, y = c, fill = abs_error_count)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_no_large_error_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "The Number of\
Large Errors\
(sd.cCI = 0.02)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot9
```

#### 8.3.2.5. Proportion of large error ~ sample size + commingling
```{r}
# Filter the data for v = 0.02
filtered_civ_0.02 <- subset(results_df_ci, v == 0.02)

# Create the categorical variable for prop_large_error ranges
filtered_civ_0.02$prop_large_error_range_civ_0.02 <- cut(filtered_civ_0.02$prop_large_error, 
                                            breaks = c(0, 0.01, 0.05, 0.1, 0.2, 1),
                                            labels = c("< 1%", "1% - 5%", "5% - 10%", "10% - 20%", "> 20%"),
                                            include.lowest = TRUE)

  
plot10 <- ggplot(filtered_civ_0.02, aes(x = n, y = c, fill = prop_large_error_range_civ_0.02)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  scale_fill_manual(values = color_palette) +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Proportion of\
Large Errors\
(sd.cCI = 0.02)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot10
```

### 8.3.3. Variation = 0.05
#### 8.3.3.1. Mean error ~ sample size + commingling
```{r}

plot11 <- ggplot(results_df_ci[results_df_ci$v == 0.05, ], aes(x = n, y = c, fill = mean_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  color_scale_mean_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Mean Errors\
(sd.cCI = 0.05)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot11
```

#### 8.3.3.2. Median absolute error ~ sample size + commingling
```{r}
plot12 <- ggplot(results_df_ci[results_df_ci$v == 0.05, ], aes(x = n, y = c, fill = median_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_median_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Median Errors\
(sd.cCI = 0.05)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot12
```

#### 8.3.3.3. Error 75%  ~ sample size + commingling
```{r}
plot13 <- ggplot(results_df_ci[results_df_ci$v == 0.05, ], aes(x = n, y = c, fill = percentile_75)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_percentile_75_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "75th Percentile\
(sd.cCI = 0.05)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot13
```

#### 8.3.3.4. Large error count ~ sample size + commingling
```{r}
plot14 <- ggplot(results_df_ci[results_df_ci$v == 0.05, ], aes(x = n, y = c, fill = abs_error_count)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_no_large_error_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "The Number of\
Large Errors\
(sd.cCI = 0.05)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot14
```

#### 8.3.3.5. Proportion of large error ~ sample size + commingling
```{r}
# Filter the data for v = 0.01
filtered_civ_0.05 <- subset(results_df_ci, v == 0.05)

# Create the categorical variable for prop_large_error ranges
filtered_civ_0.05$prop_large_error_range_civ_0.05 <- cut(filtered_civ_0.05$prop_large_error, 
                                            breaks = c(0, 0.01, 0.05, 0.1, 0.2, 1),
                                            labels = c("< 1%", "1% - 5%", "5% - 10%", "10% - 20%", "> 20%"),
                                            include.lowest = TRUE)

  
plot15 <- ggplot(filtered_civ_0.05, aes(x = n, y = c, fill = prop_large_error_range_civ_0.05)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  scale_fill_manual(values = color_palette) +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Proportion of\
Large Errors \
(sd.cCI = 0.05)
") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),
        axis.title = element_text(size = 8, face = 'bold'),
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold')) +
  scale_x_continuous(breaks = c(30, 50, 100, 150, 200, 300), labels = c("30", "50","100","150", "200","300"))

# Print
plot15
```

## 8.4. Combine the plots
### 8.4.1. Combine the BI plots
```{r}
# Combine the plots using grid.arrange
comb_bi <- grid.arrange(plot01, plot06, plot011,
                        plot02, plot07, plot012,
                        plot03, plot08, plot013, ncol = 3)
```

### 8.4.2. Combine the CI plots
```{r}
# Combine the plots using grid.arrange
comb_ci <- grid.arrange(plot1, plot6, plot11,
                        plot2, plot7, plot12,
                        plot3, plot8, plot13, ncol = 3)
```

### 8.4.2. Combine the BI and CI plots
```{r}
# Combine the plots using grid.arrange
comb_bc <- grid.arrange(plot05, plot5,
                        plot010,plot10,
                        plot015,plot15, 
                        plot016, ncol = 2)
```
