---
title: "Evaluating an Aggregate Method for Estimating Intra-Limb Proportions for Commingled Remains"
author: "Carol Doudou Cao"
date: "2023-06-08"
output: html_document
---
# Install and load necessary packages
```{r}

install.packages("tidyverse", repos = "https://cran.r-project.org/")
install.packages("viridis", repos = "https://cran.r-project.org/")
install.packages("terra", repos = "https://cran.r-project.org/")
install.packages("gridExtra", repos = "https://cran.r-project.org/") 

library(viridis)
library(tidyverse)
library(terra)
library(gridExtra)
library(scales)
```

# 1. Prepare the data
## 1.1. Read the Goldman and EU datasets

```{r}
# Goldman dataset
Goldman <- read.csv("D:/DATA SET/Data processing/AggregatedCI&BI/simulation_dataset/Goldman.csv")

# EU_Ruff
EU <- read.csv("D:/DATA SET/Data processing/AggregatedCI&BI/simulation_dataset/Ruff-European.csv")
```

## 1.2. Select the columns of interest (Assuming datasets have been loaded)
```{r}
# Select limb lengths in Goldman dataset
Goldman_selected_columns <- Goldman[, c("ID", "Sex", "NOTE", "LHML", "RHML", "LRML", "RRML", "LFBL", "RFBL", "LTML", "RTML")]

# Select limb lengths in EU_Ruff dataset
EU_selected_columns <- EU[, c("SITE", "SPECIMEN_No", "SEX", "DATE.RANGE", "YEARS.BP", "FBICLN", "TMAXLN", "HRMAXLN", "HLMAXLN", "RRMAXLN", "RLMAXLN")]
```

## 1.3. Calculate final length of the humerus (HML), radius (RML),femur (FBL) and tibia (TML)\
---Because in some limbs, the lengths of both left and right sides are reported, the final length of a limb is the averge of two sides-
```{r}
# --- Arm ---
## Goldman
### Average the maximum length of the left and right humerus 
Goldman_selected_columns$finalHML <- rowMeans(Goldman_selected_columns[, c("LHML", "RHML")], na.rm = TRUE)

### Average the maximum length of the left and right radius 
Goldman_selected_columns$finalRML <- rowMeans(Goldman_selected_columns[, c("LRML", "RRML")], na.rm = TRUE)

## EU_Ruff
### Average the maximum length of the left and right humerus 
EU_selected_columns$finalHML <- rowMeans(EU_selected_columns[, c("HRMAXLN", "HLMAXLN")], na.rm = TRUE)

### Average the maximum length of the left and right radius 
EU_selected_columns$finalRML <- rowMeans(EU_selected_columns[, c("RRMAXLN", "RLMAXLN")], na.rm = TRUE)

# --- Leg ---

## Goldman
### Average the bicondylar length of the left and right femur
Goldman_selected_columns$finalFBL <- rowMeans(Goldman_selected_columns[, c("LFBL", "RFBL")], na.rm = TRUE)

### Average the maximum length of the left and right tibia 
Goldman_selected_columns$finalTML <- rowMeans(Goldman_selected_columns[, c("LTML", "RTML")], na.rm = TRUE)
```

## 1.4. Drop rows with missing values
```{r}
# --- Arm ---
Goldman_filtered_arm <- Goldman_selected_columns[complete.cases(Goldman_selected_columns$finalHML, Goldman_selected_columns$finalRML), ]

## EU_Ruff
EU_filtered_arm <- EU_selected_columns[complete.cases(EU_selected_columns$finalHML, EU_selected_columns$finalRML), ]

# --- Leg ---
## Goldman 
Goldman_filtered_leg <- Goldman_selected_columns[complete.cases(Goldman_selected_columns$finalFBL, Goldman_selected_columns$finalTML), ]

## EU_Ruff
EU_filtered_leg <- EU_selected_columns[complete.cases(EU_selected_columns$TMAXLN, EU_selected_columns$FBICLN), ]
```

## 1.5. Filter out small-size groups (no.individuals < 5)

```{r}
# Count number of individuals per NOTE (in Goldman dataset) and SITE group (in EU_Ruff set)
# Arm
no_group_GM_arm <- table(Goldman_filtered_arm$NOTE)
no_group_EU_arm <- table(EU_filtered_arm$SITE)

# Leg
no_group_GM_leg <- table(Goldman_filtered_leg$NOTE)
no_group_EU_leg <- table(EU_filtered_leg$SITE)

# Filter out small-size groups (no.individuals < 5)
## Arm
### Goldman
Goldman_filtered_final_arm <- Goldman_filtered_arm[Goldman_filtered_arm$NOTE %in% names(no_group_GM_arm[no_group_GM_arm >= 5]), ]

### EU_Ruff
EU_filtered_final_arm <- EU_filtered_arm[EU_filtered_arm$SITE %in% names(no_group_EU_arm[no_group_EU_arm >= 5]), ]

## Leg
### Goldman
Goldman_filtered_final_leg <- Goldman_filtered_leg[Goldman_filtered_leg$NOTE %in% names(no_group_GM_leg[no_group_GM_leg >= 5]), ]

EU_filtered_final_leg <- EU_filtered_leg[EU_filtered_leg$SITE %in% names(no_group_EU_leg[no_group_EU_leg >= 5]), ]
```

## 1.6. Calculate the Conventional Brachial and Crural indices

```{r}

# Brachial index
## Goldman
Goldman_filtered_final_arm$ConventionalBI <- Goldman_filtered_final_arm$finalRML/ 
Goldman_filtered_final_arm$finalHML

## EU_Ruff
EU_filtered_final_arm$ConventionalBI <- EU_filtered_final_arm$finalRML/ 
EU_filtered_final_arm$finalHML

# Crural index
## Goldman
Goldman_filtered_final_leg$ConventionalCI <- Goldman_filtered_final_leg$finalTML / 
Goldman_filtered_final_leg$finalFBL

# Rename columns
names(EU_filtered_final_leg)[names(EU_filtered_final_leg) == "FBICLN"] <- "finalFBL"
names(EU_filtered_final_leg)[names(EU_filtered_final_leg) == "TMAXLN"] <- "finalTML"

# Calculate TrueCI
EU_filtered_final_leg$ConventionalCI <- EU_filtered_final_leg$finalTML / EU_filtered_final_leg$finalFBL
```


# 2. Create the subset of the arm and leg

## 2.1. Data cleaning and transformation operations on the Sex column of two datasets
```{r}
# Convert missing data or uncertain sex values to NA in arm dataset
Goldman_filtered_final_arm$Sex <- ifelse(Goldman_filtered_final_arm$Sex %in% c("0?", "1?"), NA, Goldman_filtered_final_arm$Sex)

# Convert 0 and 1 values to 1 and 2, respectively, in arm dataset
Goldman_filtered_final_arm$Sex <- ifelse(Goldman_filtered_final_arm$Sex == 1, 2, Goldman_filtered_final_arm$Sex)
Goldman_filtered_final_arm$Sex <- ifelse(Goldman_filtered_final_arm$Sex == 0, 1, Goldman_filtered_final_arm$Sex)

# Convert missing data or uncertain sex values to NA in leg dataset
Goldman_filtered_final_leg$Sex <- ifelse(Goldman_filtered_final_leg$Sex %in% c("0?", "1?"), NA, Goldman_filtered_final_leg$Sex)

# Convert 0 and 1 values to 1 and 2, respectively, in leg dataset
Goldman_filtered_final_leg$Sex <- ifelse(Goldman_filtered_final_leg$Sex == 1, 2, Goldman_filtered_final_leg$Sex)
Goldman_filtered_final_leg$Sex <- ifelse(Goldman_filtered_final_leg$Sex == 0, 1, Goldman_filtered_final_leg$Sex)
```

## 2.2. Create the subset of the arm and leg
```{r}
Armset <- rbind(transform(
    EU_filtered_final_arm[, c("SITE", "SEX", "SPECIMEN_No", "finalHML", "finalRML", "ConventionalBI")],
    ID = SPECIMEN_No,
    Sex = SEX,
    source = "EU"
  )[, c("SITE", "ID", "Sex", "finalHML", "finalRML", "ConventionalBI")]
,
transform(
    Goldman_filtered_final_arm[, c("NOTE", "ID", "Sex", "finalHML", "finalRML", "ConventionalBI")],
    SITE = NOTE,
    source = "Goldman"
    )[, c("SITE", "ID", "Sex", "finalHML", "finalRML", "ConventionalBI")]
  
)

# Legset
Legset <- rbind(
  transform(
    EU_filtered_final_leg[, c("SITE", "SEX", "SPECIMEN_No", "finalFBL", "finalTML", "ConventionalCI")],
    ID = SPECIMEN_No,
    Sex = SEX,
    source = "EU"
  )[, c("SITE", "Sex", "ID", "finalFBL", "finalTML", "ConventionalCI")],
  transform(
    Goldman_filtered_final_leg[, c("NOTE", "ID", "Sex", "finalTML", "finalFBL", "ConventionalCI")],
    SITE = NOTE,
    source = "Goldman",
    Sex = as.numeric(Sex)
  )[, c("SITE", "Sex", "ID", "finalFBL", "finalTML", "ConventionalCI")]
)
```

# 3. Visualise the limb lengths and indices between males and females
## 3.1. Counting males and females 
```{r}
# Counting males and females in Armset dataset
Armset_count_male <- sum(Armset$Sex == 1, na.rm = TRUE)
Armset_count_female <- sum(Armset$Sex == 2, na.rm = TRUE)

# Counting males and females  in Legset dataset
Legset_count_male  <- sum(Legset$Sex == 1, na.rm = TRUE)
Legset_count_female <- sum(Legset$Sex == 2, na.rm = TRUE)

# Print the counts
cat("Count of males in Armset:", Armset_count_male, "\n")
cat("Count of females in Armset:", Armset_count_female, "\n")
cat("Count of males in Legset:", Legset_count_male, "\n")
cat("Count of females in Legset:", Legset_count_female, "\n")
```

## 3.2. Plot the lengths and indices of males and females 
### 3.2.1 Combine the data
```{r}
# Combine the data of limb lengths
HML_male <- Armset$finalHML[Armset$Sex == 1]
HML_female <- Armset$finalHML[Armset$Sex == 2]
HML_both <- Armset$finalHML
RML_male <- Armset$finalRML[Armset$Sex == 1]
RML_female <- Armset$finalRML[Armset$Sex == 2]
RML_both <- Armset$finalRML
FBL_male <- Legset$finalFBL[Legset$Sex == 1]
FBL_female <- Legset$finalFBL[Legset$Sex == 2]
FBL_both <- Legset$finalFBL
TML_male <- Legset$finalTML[Legset$Sex == 1]
TML_female <- Legset$finalTML[Legset$Sex == 2]
TML_both <- Legset$finalTML

# Combine the data of index
BI_male <- Armset$ConventionalBI[Armset$Sex == 1]
BI_female <- Armset$ConventionalBI[Armset$Sex == 2]
BI_both <- Armset$ConventionalBI
CI_male <- Legset$ConventionalCI[Legset$Sex == 1]
CI_female <- Legset$ConventionalCI[Legset$Sex == 2]
CI_both <- Legset$ConventionalCI
```

```{r}

# Create a data frame for HML
df_HML <- data.frame(values = c(HML_male, HML_female),
                 group = rep(c("HML - Male", "HML - Female"), c(length(HML_male), length(HML_female))))

# Create the histogram for HML 
p1 <- ggplot(df_HML, aes(x = values, fill = group)) + 
  geom_histogram(binwidth = 10, alpha = 0.6, position = "identity") +
  scale_fill_manual(values = c("#d45087","skyblue" )) +
  labs(title = "", x = "HML", y = "Frequency", fill = "Sex") +
  theme_classic()+
  theme(legend.title = element_text(face = "bold", size = 12),
        legend.text = element_text(face = "bold", size = 12),
        axis.title = element_text(face = "bold", size = 14),
        axis.text =  element_text(face = "bold", size = 12))


# Create a data frame for RML
df_RML <- data.frame(values = c(RML_male, RML_female),
                 group = rep(c("RML - Male", "RML - Female"), c(length(RML_male), length(RML_female))))

# Create the histogram for RML
p2 <- ggplot(df_RML, aes(x = values, fill = group)) + 
  geom_histogram(binwidth = 10, alpha = 0.6, position = "identity") +
  scale_fill_manual(values = c( "#d45087","skyblue" )) +
  labs(title = "", x = "RML", y = "Frequency", fill = "Sex") +
  theme_classic()+
  theme(legend.title = element_text(face = "bold", size = 12),
        legend.text = element_text(face = "bold", size = 12),
        axis.title = element_text(face = "bold", size = 14),
        axis.text =  element_text(face = "bold", size = 12))


# Create a data frame for FBL
df_FBL <- data.frame(values = c(FBL_male, FBL_female),
                 group = rep(c("FBL - Male", "FBL - Female"), c(length(FBL_male), length(FBL_female))))

# Create the histogram for FBL
p3 <- ggplot(df_FBL, aes(x = values, fill = group)) + 
  geom_histogram(binwidth = 10, alpha = 0.6, position = "identity") +
  scale_fill_manual(values = c("#a05195",  "blue")) +
  labs(title = "", x = "FBL", y = "Frequency", fill = "Sex") +
  theme_classic()+
  theme(legend.title = element_text(face = "bold", size = 12),
        legend.text = element_text(face = "bold", size = 12),
        axis.title = element_text(face = "bold", size = 14),
        axis.text =  element_text(face = "bold", size = 12))

# Create a data frame for TML
df_TML <- data.frame(values = c(TML_male, TML_female),
                 group = rep(c("TML - Male", "TML - Female"), c(length(TML_male), length(TML_female))))

# Create a data frame for TML
df_TML <- data.frame(values = c(TML_male, TML_female),
                 group = rep(c("TML - Male", "TML - Female"), c(length(TML_male), length(TML_female))))

# Create the histogram for RML
p4 <- ggplot(df_TML, aes(x = values, fill = group)) + 
  geom_histogram(binwidth = 10, alpha = 0.6, position = "identity") +
  scale_fill_manual(values = c( "#a05195",  "blue")) +
  labs(title = "", x = "TML", y = "Frequency", fill = "Sex") +
  theme_classic()+
  theme(legend.title = element_text(face = "bold", size = 12),
        legend.text = element_text(face = "bold", size = 12),
        axis.title = element_text(face = "bold", size = 14),
        axis.text =  element_text(face = "bold", size = 12))

# Create a data frame for BI
df_BI <- subset(data.frame(values = c(BI_male, BI_female),
                 group = rep(c("BIt - Male", "BIt - Female"), c(length(BI_male), length(BI_female)))),
               values > 0.6 & values < 0.99)

# Create the histogram for BIt 

p5 <- ggplot(df_BI, aes(x = values, fill = group)) + 
  geom_histogram(binwidth = 0.01, alpha = 0.6, position = "identity") +
  scale_fill_manual(values = c("#d45087", "skyblue")) +
  labs(title = "", x = "BIc", y = "Frequency", fill = "Sex") +
  theme_classic() +
  theme(
    legend.title = element_text(face = "bold", size = 14),
    legend.text = element_text(face = "bold", size = 14),
    axis.title = element_text(face = "bold", size = 18),
    axis.text =  element_text(face = "bold", size = 14)) +
    scale_x_continuous(breaks = seq(0, 1, by = 0.05))

# Create a data frame for CI
df_CI <- subset(data.frame(values = c(CI_male, CI_female),
                 group = rep(c("CIt - Male", "CIt - Female"), c(length(CI_male), length(CI_female)))), values < 1)

# Create the histogram for CIt
p6 <- ggplot(df_CI, aes(x = values, fill = group)) + 
  geom_histogram(binwidth = 0.01, alpha = 0.6, position = "identity") +
  scale_fill_manual(values = c( "#a05195",  "blue")) +
  labs(title = "", x = "CIc", y = "Frequency", fill = "Sex") +
  theme_classic()+
  theme(legend.title = element_text(face = "bold", size = 14),
        legend.text = element_text(face = "bold", size = 14),
        axis.title = element_text(face = "bold", size = 18),
        axis.text =  element_text(face = "bold", size = 14))

# Create the combined plot
combined_histogram_limblength <- grid.arrange(p1, p2, p3, p4, ncol = 2,nrow = 2)
combined_histogram_indices <- grid.arrange(p5, p6, ncol = 2)
combined_histogram_limblength_indices <- grid.arrange(p1, p2, p3, p4, p5, p6, ncol = 2)
```

# 4. Summarise the limb lengths and indices
## 4.1. Summarise the limb lengths 
### 4.1.1. Summarise the limb lengths (combined)
```{r}
# Humerus
Mean_HML <- aggregate(Armset$finalHML, by = list(Armset$SITE), FUN = mean)
colnames(Mean_HML) <- c("SITE", "mean_finalHML")

summary_HML <- data.frame(
  mean_mean_finalHML = mean(Mean_HML$mean_finalHML),
  max_mean_finalHML = max(Mean_HML$mean_finalHML),
  min_mean_finalHML = min(Mean_HML$mean_finalHML),
  sd_mean_finalHML = sd(Mean_HML$mean_finalHML)
)

# Radius
Mean_RML <- aggregate(Armset$finalRML, by = list(Armset$SITE), FUN = mean)
colnames(Mean_RML) <- c("SITE", "mean_finalRML")

summary_RML <- data.frame(
  mean_mean_finalRML = mean(Mean_RML$mean_finalRML),
  max_mean_finalRML = max(Mean_RML$mean_finalRML),
  min_mean_finalRML = min(Mean_RML$mean_finalRML),
  sd_mean_finalRML = sd(Mean_RML$mean_finalRML)
)

# Femur
Mean_FBL <- aggregate(Legset$finalFBL, by = list(Legset$SITE), FUN = mean)
colnames(Mean_FBL) <- c("SITE", "mean_finalFBL")

summary_FBL <- data.frame(
  mean_mean_finalFBL = mean(Mean_FBL$mean_finalFBL),
  max_mean_finalFBL = max(Mean_FBL$mean_finalFBL),
  min_mean_finalFBL = min(Mean_FBL$mean_finalFBL),
  sd_mean_finalFBL = sd(Mean_FBL$mean_finalFBL)
)

# Tibia
Mean_TML <- aggregate(Legset$finalTML, by = list(Legset$SITE), FUN = mean)
colnames(Mean_TML) <- c("SITE", "mean_finalTML")

summary_TML <- data.frame(
  mean_mean_finalTML = mean(Mean_TML$mean_finalTML),
  max_mean_finalTML = max(Mean_TML$mean_finalTML),
  min_mean_finalTML = min(Mean_TML$mean_finalTML),
  sd_mean_finalTML = sd(Mean_TML$mean_finalTML)
)

# Print summary statistics
print(summary_HML)
print(summary_RML)
print(summary_FBL)
print(summary_TML)
```

### 4.1.2. Summarise the limb lengths (by sex)
```{r}
# Humerus
## Male
Mean_HML_male <- aggregate(finalHML ~ SITE, data = Armset[Armset$Sex == 1, ], FUN = mean)
colnames(Mean_HML_male) <- c("SITE", "mean_finalHML_male")

summary_HML_male <- data.frame(
  mean_mean_finalHML_male = mean(Mean_HML_male$mean_finalHML_male),
  max_mean_finalHML_male = max(Mean_HML_male$mean_finalHML_male),
  min_mean_finalHML_male = min(Mean_HML_male$mean_finalHML_male),
  sd_mean_finalHML_male = sd(Mean_HML_male$mean_finalHML_male)
)

## Female
Mean_HML_female <- aggregate(finalHML ~ SITE, data = Armset[Armset$Sex == 2, ], FUN = mean)
colnames(Mean_HML_female) <- c("SITE", "mean_finalHML_female")

summary_HML_female <- data.frame(
  mean_mean_finalHML_female = mean(Mean_HML_female$mean_finalHML_female),
  max_mean_finalHML_female = max(Mean_HML_female$mean_finalHML_female),
  min_mean_finalHML_female = min(Mean_HML_female$mean_finalHML_female),
  sd_mean_finalHML_female = sd(Mean_HML_female$mean_finalHML_female)
)

# Radius
## Male
Mean_RML_male <- aggregate(finalRML ~ SITE, data = Armset[Armset$Sex == 1, ], FUN = mean)
colnames(Mean_RML_male) <- c("SITE", "mean_finalRML_male")

summary_RML_male <- data.frame(
  mean_mean_finalRML_male = mean(Mean_RML_male$mean_finalRML_male),
  max_mean_finalRML_male = max(Mean_RML_male$mean_finalRML_male),
  min_mean_finalRML_male = min(Mean_RML_male$mean_finalRML_male),
  sd_mean_finalRML_male = sd(Mean_RML_male$mean_finalRML_male)
)

## Female
Mean_RML_female <- aggregate(finalRML ~ SITE, data = Armset[Armset$Sex == 2, ], FUN = mean)
colnames(Mean_RML_female) <- c("SITE", "mean_finalRML_female")

summary_RML_female <- data.frame(
  mean_mean_finalRML_female = mean(Mean_RML_female$mean_finalRML_female),
  max_mean_finalRML_female = max(Mean_RML_female$mean_finalRML_female),
  min_mean_finalRML_female = min(Mean_RML_female$mean_finalRML_female),
  sd_mean_finalRML_female = sd(Mean_RML_female$mean_finalRML_female)
)

# Femur
## Male
Mean_FBL_male <- aggregate(finalFBL ~ SITE, data = Legset[Legset$Sex == 1, ], FUN = mean)
colnames(Mean_FBL_male) <- c("SITE", "mean_finalFBL_male")

summary_FBL_male <- data.frame(
  mean_mean_finalFBL_male = mean(Mean_FBL_male$mean_finalFBL_male),
  max_mean_finalFBL_male = max(Mean_FBL_male$mean_finalFBL_male),
  min_mean_finalFBL_male = min(Mean_FBL_male$mean_finalFBL_male),
  sd_mean_finalFBL_male = sd(Mean_FBL_male$mean_finalFBL_male)
)

## Female
Mean_FBL_female <- aggregate(finalFBL ~ SITE, data = Legset[Legset$Sex == 2, ], FUN = mean)
colnames(Mean_FBL_female) <- c("SITE", "mean_finalFBL_female")

summary_FBL_female <- data.frame(
  mean_mean_finalFBL_female = mean(Mean_FBL_female$mean_finalFBL_female),
  max_mean_finalFBL_female = max(Mean_FBL_female$mean_finalFBL_female),
  min_mean_finalFBL_female = min(Mean_FBL_female$mean_finalFBL_female),
  sd_mean_finalFBL_female = sd(Mean_FBL_female$mean_finalFBL_female)
)

# Tibia
## Male
Mean_TML_male <- aggregate(finalTML ~ SITE, data = Legset[Legset$Sex == 1, ], FUN = mean)
colnames(Mean_TML_male) <- c("SITE", "mean_finalTML_male")

summary_TML_male <- data.frame(
  mean_mean_finalTML_male = mean(Mean_TML_male$mean_finalTML_male),
  max_mean_finalTML_male = max(Mean_TML_male$mean_finalTML_male),
  min_mean_finalTML_male = min(Mean_TML_male$mean_finalTML_male),
  sd_mean_finalTML_male = sd(Mean_TML_male$mean_finalTML_male)
)

## Female
Mean_TML_female <- aggregate(finalTML ~ SITE, data = Legset[Legset$Sex == 2, ], FUN = mean)
colnames(Mean_TML_female) <- c("SITE", "mean_finalTML_female")

summary_TML_female <- data.frame(
  mean_mean_finalTML_female = mean(Mean_TML_female$mean_finalTML_female),
  max_mean_finalTML_female = max(Mean_TML_female$mean_finalTML_female),
  min_mean_finalTML_female = min(Mean_TML_female$mean_finalTML_female),
  sd_mean_finalTML_female = sd(Mean_TML_female$mean_finalTML_female)
)

# Print summary statistics
summary_HML_male
summary_HML_female
summary_RML_male
summary_RML_female
summary_FBL_male
summary_FBL_female
summary_TML_male
summary_TML_female
```

## 4.2 Summarise the indices
### 4.2.1. Summarise the indices (combined)
```{r}
# Brachial index
## Mean_BIc
Mean_BIc <- aggregate(Armset$ConventionalBI, by = list(Armset$SITE), FUN = mean)
colnames(Mean_BIc) <- c("SITE", "mean_BIc")

summary_mean_BIc <- data.frame(
  mean_mean_BIc = mean(Mean_BIc$mean_BIc),
  max_mean_BIc = max(Mean_BIc$mean_BIc),
  min_mean_BIc = min(Mean_BIc$mean_BIc),
  sd_mean_BIc = sd(Mean_BIc$mean_BIc)
)

## SD_BIc
SD_BIc <- aggregate(Armset$ConventionalBI, by = list(Armset$SITE), FUN = sd)
colnames(SD_BIc) <- c("SITE", "sd_BIc")

summary_sd_BIc <- data.frame(
  mean_sd_BIc = mean(SD_BIc$sd_BIc),
  max_sd_BIc = max(SD_BIc$sd_BIc),
  min_sd_BIc = min(SD_BIc$sd_BIc),
  sd_sd_BIc = sd(SD_BIc$sd_BIc)
)


# Crural index
## Mean_CIt
Mean_CIc <- aggregate(Legset$ConventionalCI, by = list(Legset$SITE), FUN = mean)
colnames(Mean_CIc) <- c("SITE", "mean_CIc")

summary_mean_CIc <- data.frame(
  mean_mean_CIc = mean(Mean_CIc$mean_CIc),
  max_mean_CIc = max(Mean_CIc$mean_CIc),
  min_mean_CIc = min(Mean_CIc$mean_CIc),
  sd_mean_CIc = sd(Mean_CIc$mean_CIc)
)

## SD_CIt
SD_CIc <- aggregate(Legset$ConventionalCI, by = list(Legset$SITE), FUN = sd)
colnames(SD_CIc) <- c("SITE", "sd_CIc")

summary_sd_CIc <- data.frame(
  mean_sd_CIc = mean(SD_CIc$sd_CIc),
  max_sd_CIc = max(SD_CIc$sd_CIc),
  min_sd_CIc = min(SD_CIc$sd_CIc),
  sd_sd_CIc = sd(SD_CIc$sd_CIc)
)

# Print summary statistics
summary_mean_BIc
summary_mean_CIc
summary_sd_BIc
summary_sd_CIc
```

### 4.2.2. Summarise the indices (by sex)
```{r}

# Brachial index
## Mean_BIc 
### Male
Mean_BIc_male <- aggregate(ConventionalBI ~ SITE, data = Armset[Armset$Sex == 1, ], FUN = mean)
colnames(Mean_BIc_male) <- c("SITE", "mean_BIc_male")

summary_mean_BIc_male <- data.frame(
  mean_mean_BIc_male = mean(Mean_BIc_male$mean_BIc_male),
  max_mean_BIc_male = max(Mean_BIc_male$mean_BIc_male),
  min_mean_BIc_male = min(Mean_BIc_male$mean_BIc_male),
  sd_mean_BIc_male = sd(Mean_BIc_male$mean_BIc_male)
)

## SD_BIc 
### Male
SD_BIc_male <- aggregate(ConventionalBI ~ SITE, data = Armset[Armset$Sex == 1, ], FUN = sd)
colnames(SD_BIc_male) <- c("SITE", "sd_BIc_male")

summary_sd_BIc_male <- data.frame(
  mean_sd_BIc_male = mean(SD_BIc_male$sd_BIc_male, na.rm = TRUE),
  max_sd_BIc_male = max(SD_BIc_male$sd_BIc_male, na.rm = TRUE),
  min_sd_BIc_male = min(SD_BIc_male$sd_BIc_male, na.rm = TRUE),
  sd_sd_BIc_male = sd(SD_BIc_male$sd_BIc_male, na.rm = TRUE)
)

#### Female
Mean_BIc_female <- aggregate(ConventionalBI ~ SITE, data = Armset[Armset$Sex == 2, ], FUN = mean)
colnames(Mean_BIc_female) <- c("SITE", "mean_BIc_female")

summary_mean_BIc_female <- data.frame(
  mean_mean_BIc_female = mean(Mean_BIc_female$mean_BIc_female),
  max_mean_BIc_female = max(Mean_BIc_female$mean_BIc_female),
  min_mean_BIc_female = min(Mean_BIc_female$mean_BIc_female),
  sd_mean_BIc_female = sd(Mean_BIc_female$mean_BIc_female)
)

### SD_BIt 
SD_BIc_female <- aggregate(ConventionalBI ~ SITE, data = Armset[Armset$Sex == 2, ], FUN = sd)
colnames(SD_BIc_female) <- c("SITE", "sd_BIc_female")

summary_sd_BIc_female <- data.frame(
  mean_sd_BIc_female = mean(SD_BIc_female$sd_BIc_female, na.rm = TRUE),
  max_sd_BIc_female = max(SD_BIc_female$sd_BIc_female, na.rm = TRUE),
  min_sd_BIc_female = min(SD_BIc_female$sd_BIc_female, na.rm = TRUE),
  sd_sd_BIc_female = sd(SD_BIc_female$sd_BIc_female, na.rm = TRUE)
)

## Crural index

### Male
#### Mean_CIc
Mean_CIc_male <- aggregate(Legset$ConventionalCI[Legset$Sex == 1], by = list(Legset$SITE[Legset$Sex == 1]), FUN = mean)
colnames(Mean_CIc_male) <- c("SITE", "mean_CIc_male")

summary_mean_CIc_male <- data.frame(
  mean_mean_CIc_male = mean(Mean_CIc_male$mean_CIc_male),
  max_mean_CIc_male = max(Mean_CIc_male$mean_CIc_male),
  min_mean_CIc_male = min(Mean_CIc_male$mean_CIc_male),
  sd_mean_CIc_male = sd(Mean_CIc_male$mean_CIc_male)
)

#### SD_CIc 
SD_CIc_male <- aggregate(Legset$ConventionalCI[Legset$Sex == 1], by = list(Legset$SITE[Legset$Sex == 1]), FUN = sd)
colnames(SD_CIc_male) <- c("SITE", "sd_CIc_male")

summary_sd_CIc_male <- data.frame(
  mean_sd_CIc_male = mean(SD_CIc_male$sd_CIc_male, na.rm = TRUE),
  max_sd_CIc_male = max(SD_CIc_male$sd_CIc_male, na.rm = TRUE),
  min_sd_CIc_male = min(SD_CIc_male$sd_CIc_male, na.rm = TRUE),
  sd_sd_CIc_male = sd(SD_CIc_male$sd_CIc_male, na.rm = TRUE)
)

### Female
#### Mean_CIc
Mean_CIc_female <- aggregate(Legset$ConventionalCI[Legset$Sex == 2], by = list(Legset$SITE[Legset$Sex == 2]), FUN = mean)
colnames(Mean_CIc_female) <- c("SITE", "mean_CIc_female")

summary_mean_CIc_female <- data.frame(
  mean_mean_CIc_female = mean(Mean_CIc_female$mean_CIc_female),
  max_mean_CIc_female = max(Mean_CIc_female$mean_CIc_female),
  min_mean_CIc_female = min(Mean_CIc_female$mean_CIc_female),
  sd_mean_CIc_female = sd(Mean_CIc_female$mean_CIc_female)
)

#### SD_CIc 
SD_CIc_female <- aggregate(Legset$ConventionalCI[Legset$Sex == 2], by = list(Legset$SITE[Legset$Sex == 2]), FUN = sd)
colnames(SD_CIc_female) <- c("SITE", "sd_CIc_female")

summary_sd_CIc_female <- data.frame(
  mean_sd_CIc_female = mean(SD_CIc_female$sd_CIc_female, na.rm = TRUE),
  max_sd_CIc_female = max(SD_CIc_female$sd_CIc_female, na.rm = TRUE),
  min_sd_CIc_female = min(SD_CIc_female$sd_CIc_female, na.rm = TRUE),
  sd_sd_CIc_female = sd(SD_CIc_female$sd_CIc_female, na.rm = TRUE)
)


# Print summary statistics
summary_mean_BIc_male
summary_mean_CIc_male
summary_sd_BIc_male
summary_sd_CIc_male
summary_mean_BIc_female
summary_mean_CIc_female
summary_sd_BIc_female
summary_sd_CIc_female
```

# 5. Compare the limb lengths and indices between males and females
## 5.1. Conduct t-tests on the limb lengths
```{r}
results_ttest_limblength <- data.frame()

# Conduct t-tests for limb lengths between males and females at each site
for (site in unique(Armset$SITE)) {
  male_hml <- subset(Armset, Sex == 1 & SITE == site)$finalHML
  female_hml <- subset(Armset, Sex == 2 & SITE == site)$finalHML
  male_rml <- subset(Armset, Sex == 1 & SITE == site)$finalRML
  female_rml <- subset(Armset, Sex == 2 & SITE == site)$finalRML

  male_fbl <- subset(Legset, Sex == 1 & SITE == site)$finalFBL
  female_fbl <- subset(Legset, Sex == 2 & SITE == site)$finalFBL
  male_tml <- subset(Legset, Sex == 1 & SITE == site)$finalTML
  female_tml <- subset(Legset, Sex == 2 & SITE == site)$finalTML

  if (length(male_hml) >= 3 & length(female_hml) >= 3 & length(male_rml) >= 3 & length(female_rml) >= 3 & length(male_fbl) >= 3 & length(female_fbl) >= 3 & length(male_tml) >= 3 & length(female_tml) >= 3) {
    ttest_hml <- t.test(male_hml, female_hml)
    ttest_rml <- t.test(male_rml, female_rml)
    ttest_fbl <- t.test(male_fbl, female_fbl)
    ttest_tml <- t.test(male_tml, female_tml)

    results_ttest_limblength <- rbind(results_ttest_limblength,
                                      data.frame(Site = site,
                                                 Variable = c("HML", "RML", "FBL", "TML"),
                                                 Group = rep("Male vs. Female", 4),
                                                 t_statistic = c(ttest_hml$statistic, ttest_rml$statistic, ttest_fbl$statistic, ttest_tml$statistic),
                                                 p_value = c(ttest_hml$p.value, ttest_rml$p.value, ttest_fbl$p.value, ttest_tml$p.value))
    )
  }
}

# HML
num_sig_ttests_HML <- sum(results_ttest_limblength$Variable == 'HML' & results_ttest_limblength$p_value < 0.05)
cat("Number of significant T-tests for HML:", num_sig_ttests_HML, "\n")

num_nonsig_ttests_HML <- sum(results_ttest_limblength$Variable == 'HML' & results_ttest_limblength$p_value >= 0.05)
cat("Number of non-significant T-tests for HML:", num_nonsig_ttests_HML, "\n")

# RML
num_sig_ttests_RML <- sum(results_ttest_limblength$Variable == 'RML' & results_ttest_limblength$p_value < 0.05)
cat("Number of significant T-tests for RML:", num_sig_ttests_RML, "\n")

num_nonsig_ttests_RML <- sum(results_ttest_limblength$Variable == 'RML' & results_ttest_limblength$p_value >= 0.05)
cat("Number of non-significant T-tests for RML:", num_nonsig_ttests_RML, "\n")

# FBL
num_sig_ttests_FBL <- sum(results_ttest_limblength$Variable == 'FBL' & results_ttest_limblength$p_value < 0.05)
cat("Number of significant T-tests for FBL:", num_sig_ttests_FBL, "\n")

num_nonsig_ttests_FBL <- sum(results_ttest_limblength$Variable == 'FBL' & results_ttest_limblength$p_value >= 0.05)
cat("Number of non-significant T-tests for FBL:", num_nonsig_ttests_FBL, "\n")

# TML
num_sig_ttests_TML <- sum(results_ttest_limblength$Variable == 'TML' & results_ttest_limblength$p_value < 0.05)
cat("Number of significant T-tests for TML:", num_sig_ttests_TML, "\n")

num_nonsig_ttests_TML <- sum(results_ttest_limblength$Variable == 'TML' & results_ttest_limblength$p_value >= 0.05)
cat("Number of non-significant T-tests for TML:", num_nonsig_ttests_TML, "\n")
```

## 5.2. Conduct t-tests on the indices
```{r}
results_ttest_BC <- data.frame()

# Conduct t-tests for BI and CI between males and females at each site
for (site in unique(Armset$SITE)) {
  male_bic <- subset(Armset, Sex == 1 & SITE == site)$ConventionalBI
  female_bic <- subset(Armset, Sex == 2 & SITE == site)$ConventionalBI
  male_cic <- subset(Legset, Sex == 1 & SITE == site)$ConventionalCI
  female_cic <- subset(Legset, Sex == 2 & SITE == site)$ConventionalCI

  if (length(male_bic) >= 3 & length(female_bic) >= 3 & length(male_cic) >= 3 & length(female_cic) >= 3) {
    ttest_bic <- t.test(male_bic, female_bic)
    ttest_cic <- t.test(male_cic, female_cic)

    results_ttest_BC <- rbind(results_ttest_BC,
                              data.frame(Site = site,
                                         Variable = c("BIc", "CIc"),
                                         Group = rep("Male vs. Female", 2),
                                         t_statistic = c(ttest_bic$statistic, ttest_cic$statistic),
                                         p_value = c(ttest_bic$p.value, ttest_cic$p.value))
    )
  }
}

# Count the number of significant and non-significant t-tests
num_sig_ttests_BIc <- sum(results_ttest_BC$Variable == 'BIc' & results_ttest_BC$p_value < 0.05)
cat("Number of significant T-tests for BIc:", num_sig_ttests_BIc, "\n")

num_nonsig_ttests_BIc <- sum(results_ttest_BC$Variable == 'BIc' & results_ttest_BC$p_value >= 0.05)
cat("Number of non-significant T-tests for BIc:", num_nonsig_ttests_BIc, "\n")

num_sig_ttests_CIc <- sum(results_ttest_BC$Variable == 'CIc' & results_ttest_BC$p_value < 0.05)
cat("Number of significant T-tests for CIc:", num_sig_ttests_CIc, "\n")

num_nonsig_ttests_CIc <- sum(results_ttest_BC$Variable == 'CIc' & results_ttest_BC$p_value >= 0.05)
cat("Number of non-significant T-tests for CIc:", num_nonsig_ttests_CIc, "\n")
```

# 6. Compare the conventional and aggregated indices without the simulation 
## 6.1. Compute averages of conventinal values and mean limb lengths for each site
```{r}
res_arm <- aggregate(cbind(finalHML,finalRML,ConventionalBI)~SITE,data=Armset,mean)
res_leg <- aggregate(cbind(finalFBL,finalTML,ConventionalCI)~SITE,data=Legset,mean)
```

## 6.2. compute conventional indices obtained from the mean limb lengths

```{r}
res_arm$BIa <- res_arm$finalRML/res_arm$finalHML
res_leg$CIa <- res_leg$finalTML/res_leg$finalFBL
```

## 6.3. Linear regression
```{r}
# Fit the linear regression model
lm_model_bi <- lm(BIa ~ ConventionalBI, data = res_arm)
lm_model_ci <- lm(CIa ~ ConventionalCI, data = res_leg)

# Print the model summary
summary(lm_model_bi)
summary(lm_model_ci)
```

## 6.4. Plot
```{r}
# Scatter plot with linear regression line for BIa vs. BIc
plot_bi <- ggplot(data = res_arm, aes(x = ConventionalBI, y = BIa)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "#d45087") +
  labs(title = "BIc vs. BIa", x = "BIc", y = "BIa")+
  theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 14))

# Scatter plot with linear regression line for CIa vs. CIc
plot_ci <- ggplot(data = res_leg, aes(x = ConventionalCI, y = CIa)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "steelblue") +
  labs(title = "CIc vs. CIa", x = "CIc", y = "CIa")+
  theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 14))

# Combine the plots
combined_indices <- grid.arrange(plot_bi, plot_ci, ncol = 2,nrow = 1)
```


# 7. Simulating Three Commingling Conditions 
## 7.1. Function for calculating and comparing the aggregated and conventional indices
### 7.1.1 BIc vs. BIa
```{r}
simFun_bi <- function(n1,n2,mean.hml,sd.hml,sd.bi,mean.bi,nsim)
{
  est.bi  <- numeric(length=nsim) #just a placeholder vector for storing estimates
  for (i in 1:nsim) #main simulation loop
  {
    #Simulate paired individuals
    hml.paired  <- rnorm(n1/2,mean=mean.hml,sd=sd.hml)
    bi.paired  <- rnorm(n1/2,mean=mean.bi,sd=sd.bi)
    rml.paired  <- hml.paired * bi.paired
    #Simulate unpaired individuals
    hml.unpaired  <- rnorm(n2/2,mean=mean.hml,sd=sd.hml) 
    #Simulate half the femur as normal
    rml.unpaired  <- rnorm(n2/2,mean=mean.hml,sd=sd.hml) * rnorm(n2/2,mean=mean.bi,sd=sd.bi) #Simulate another set of femurs but store only their corresponding Tibia after drawing other crural index values
    #Combine
    hml <- c(hml.paired,hml.unpaired)
    rml <- c(rml.paired,rml.unpaired)
    #Estimate
    est.bi[i]  <- mean(rml)/mean(hml)
  }
  return(list(true.bi=mean.bi,est.bi=est.bi,error=est.bi-mean.bi))
}
```

### 7.1.2 CIc vs. CIa
```{r}
simFun_ci <- function(n1,n2,mean.fbl,sd.fbl,sd.ci,mean.ci,nsim)
{
  est.ci  <- numeric(length=nsim) #just a placeholder vector for storing estimates
  for (i in 1:nsim) #main simulaion loop
  {
    #Simulate paired individuals
    fbl.paired  <- rnorm(n1/2,mean=mean.fbl,sd=sd.fbl)
    ci.paired  <- rnorm(n1/2,mean=mean.ci,sd=sd.ci)
    tml.paired  <- fbl.paired * ci.paired
    #Simulate unpaired individuals
    fbl.unpaired  <- rnorm(n2/2,mean=mean.fbl,sd=sd.fbl) 
    #Simulate half the femur as normal
    tml.unpaired  <- rnorm(n2/2,mean=mean.fbl,sd=sd.fbl) * rnorm(n2/2,mean=mean.ci,sd=sd.ci) #Simulate another set of femurs but store only their corresponding Tibia after drawing other crural index values
    #Combine
    fbl <- c(fbl.paired,fbl.unpaired)
    tml <- c(tml.paired,tml.unpaired)
    #Estimate
    est.ci[i]  <- mean(tml)/mean(fbl)
  }
  return(list(true.ci=mean.ci,est.ci=est.ci,error=est.ci-mean.ci)) # 
}
```

## 7.2. Function for simulating the sample size (n), commingling (c) and variation (v)
### 7.2.1. Simulate the BI
```{r}
# Create grid of parameter combinations to simulate
n <- seq(10, 300, length.out = 30) # Sample size
c <- seq(0, 1, length.out = 30)    # Commingling Degree
v <- c(0.01, 0.02, 0.08) # Within-group Variation in the Brachial index
parm <- expand.grid(n, c, v)

# Modify simulate function to run simulation 10000 times
simulate <- function(parms, n_sims = 10000) {
  # Extract parameters from parms
  n <- parms[1]
  c <- parms[2]
  v <- parms[3]
  
  # Round n to the nearest even number
  n <- round(n/2) * 2
  
  # Initialize variables to store results
  error_set <- numeric(n_sims)
  
  # Run simulations
  for (i in 1:n_sims) {
    # Call the simFun_ci function with the specified parameters
    sim_result <- simFun_bi(n1 = round(n*(1-c)), n2 = round(n*c), mean.hml=308.73,sd.hml=13.24, sd.bi = v, mean.bi = 0.7597, nsim = 1)
    
    # Compute error
    error <- abs(sim_result$error)
    
    # Store results
    error_set[i] <- sim_result$error
  }
  
 # Compute summary statistics of the errors
   mean_abs_error <- abs(mean(error_set)) #  the absolute value of the mean
   median_abs_error <- abs(median(error_set)) # absolute value of the median_error
   percentile_75 <- abs(quantile(error_set, probs = 0.75, na.rm = TRUE))# Compute the 75th percentile of the errors
   
   # Compute values that are greater than 0.02
    abs_error_count <- sum(abs(error_set) > 0.02, na.rm = TRUE) # the number of errors in the error_set that have an absolute value greater than 0.02, excluding any NA values.
    # the proportion of simulations where the absolute value of the median_error is greater than 0.02
    prop_large_error <- abs_error_count / sum(!is.na(error_set))

   # Create data frame with results and parameters
   results_df_bi <- data.frame(n = n, c = c, v = v, 
                              mean_abs_error = mean_abs_error,median_abs_error = median_abs_error, percentile_75=percentile_75, 
                              abs_error_count = abs_error_count, prop_large_error = prop_large_error)

  return(results_df_bi)
}

# Run simulation and store results in a data frame
set.seed(123) # set seed for reproducibility
results_bi <- replicate(1, apply(parm, 1, simulate), simplify = FALSE)
results_df_bi <- bind_rows(results_bi)
```

### 7.2.1. Simulate the CI
```{r}
# Create grid of parameter combinations to simulate
n <- seq(10, 300, length.out = 30) # Sample size
c <- seq(0, 1, length.out = 30)    # Commingling Degree
v <- c(0.01, 0.02, 0.05) # Within-group Variation in the Crural index
parm <- expand.grid(n, c, v)

# Modify simulate function to run simulation 10000 times
simulate <- function(parms, n_sims = 10000) {
  # Extract parameters from parms
  n <- parms[1]
  c <- parms[2]
  v <- parms[3]
  
  # Round n to the nearest even number
  n <- round(n/2) * 2
  
  # Initialize variables to store results
  error_set <- numeric(n_sims)
  
  # Run simulations
  for (i in 1:n_sims) {
    # Call the simFun_ci function with the specified parameters
    sim_result <- simFun_ci(n1 = round(n*(1-c)), n2 = round(n*c), mean.fbl=426.64,sd.fbl=26.07, sd.ci = v, mean.ci = 0.8348, nsim = 1)
    
    # Compute error
    error <- abs(sim_result$error)
    
    # Store results
    error_set[i] <- sim_result$error
  }
  
   # Compute summary statistics of the errors
   mean_abs_error <- abs(mean(error_set)) #  the absolute value of the mean
   median_abs_error <- abs(median(error_set)) # absolute value of the median_error
   percentile_75 <- abs(quantile(error_set, probs = 0.75, na.rm = TRUE))# Compute the 75th percentile of the errors
   
   # Compute values that are greater than 0.02
    abs_error_count <- sum(abs(error_set) > 0.02, na.rm = TRUE) # the number of errors in the error_set that have an absolute value greater than 0.02, excluding any NA values.
    # the proportion of simulations where the absolute value of the median_error is greater than 0.02
    prop_large_error <- abs_error_count / sum(!is.na(error_set))
    

   # Create data frame with results and parameters
   results_df_ci <- data.frame(n = n, c = c, v = v, 
                              mean_abs_error = mean_abs_error,median_abs_error = median_abs_error, percentile_75=percentile_75, 
                              abs_error_count = abs_error_count, prop_large_error = prop_large_error)

  return(results_df_ci)
}

# Run simulation and store results in a data frame
set.seed(123) # set seed for reproducibility
results_ci <- replicate(1, apply(parm, 1, simulate), simplify = FALSE)
results_df_ci <- bind_rows(results_ci)
```

# 8. Plot
## 8.1. Set the parameter for indicative lines and common colour scale for each graph
```{r}
# parameter for indicative lines
simulated_n <- c (30, 50, 100)
simulated_c <- c (0.25, 0.5, 0.75)

# Find the common color scale limits for different sets of plots (mean, median, 75 percentile, and the number as well as proportion of large errors)
## BI
color_scale_mean_bi <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_bi$mean_abs_error), max(results_df_bi$mean_abs_error)))
color_scale_median_bi <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_bi$median_abs_error), max(results_df_bi$median_abs_error)))
color_scale_percentile_75_bi <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_bi$percentile_75), max(results_df_bi$percentile_75)))
color_scale_no_large_error_bi <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_bi$abs_error_count), max(results_df_bi$abs_error_count)))
color_scale_prop_large_error_bi <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_bi$prop_large_error), max(results_df_bi$prop_large_error)))

## CI
color_scale_mean_ci <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_ci$mean_abs_error), max(results_df_ci$mean_abs_error)))
color_scale_median_ci <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_ci$median_abs_error), max(results_df_ci$median_abs_error)))
color_scale_percentile_75_ci <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_ci$percentile_75), max(results_df_ci$percentile_75)))
color_scale_no_large_error_ci <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_ci$abs_error_count), max(results_df_ci$abs_error_count)))
color_scale_prop_large_error_ci <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_ci$prop_large_error), max(results_df_ci$prop_large_error)))
```

## 8.2. Plot-BI
### 8.2.1.Variation = 0.01
#### 8.2.1.1. Mean error ~ sample size + commingling
```{r}
plot01 <- ggplot(results_df_bi[results_df_bi$v == 0.01, ], aes(x = n, y = c, fill = mean_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  color_scale_mean_bi +
  xlab('Sample Size') +
  ylab('Commingling degree') +
  labs(fill = "Mean Errors\
(sd.bi = 0.01)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot01
```

#### 8.2.1.2. Median absolute error ~ sample size + commingling
```{r}
plot02 <- ggplot(results_df_bi[results_df_bi$v == 0.01, ], aes(x = n, y = c, fill = median_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_median_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Median Errors\
(sd.bi = 0.01)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot02
```

#### 8.2.1.3. Error 75%  ~ sample size + commingling
```{r}
plot03 <- ggplot(results_df_bi[results_df_bi$v == 0.01, ], aes(x = n, y = c, fill = percentile_75)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_percentile_75_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "75th Percentile\
(sd.bi = 0.01)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot03
```

#### 8.2.1.4.  Large error count ~ sample size + commingling
```{r}
plot04 <- ggplot(results_df_bi[results_df_bi$v == 0.01, ], aes(x = n, y = c, fill = abs_error_count)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_no_large_error_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "The Number of\
Large Errors(> 0.02,\
sd.bi = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot04
```

#### 8.2.1.5.  Proportion of large error ~ sample size + commingling
```{r}
plot05 <- ggplot(results_df_bi[results_df_bi$v == 0.01, ], aes(x = n, y = c, fill = prop_large_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_prop_large_error_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Proportion of\
Large Errors\
(sd.bi = 0.01)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))
# Print
plot05
```

### 8.2.2. Variation = 0.02
#### 8.2.2.1. Mean error ~ sample size + commingling
```{r}
plot06 <- ggplot(results_df_bi[results_df_bi$v == 0.02, ], aes(x = n, y = c, fill = mean_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  color_scale_mean_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Mean Errors\
(sd.bi = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot06
```

#### 8.2.2.2. Median absolute error ~ sample size + commingling
```{r}
plot07 <- ggplot(results_df_bi[results_df_bi$v == 0.02, ], aes(x = n, y = c, fill = median_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_median_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Median Errors\
(sd.bi = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot07
```

#### 8.2.2.3. Error 75%  ~ sample size + commingling
```{r}
plot08 <- ggplot(results_df_bi[results_df_bi$v == 0.02, ], aes(x = n, y = c, fill = percentile_75)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_percentile_75_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "75th Percentile\
(sd.bi = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot08     
```

#### 8.2.2.4. Large error count ~ sample size + commingling
```{r}
plot09 <- ggplot(results_df_bi[results_df_bi$v == 0.02, ], aes(x = n, y = c, fill = abs_error_count)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_no_large_error_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "The Number of\
Large Error (> 0.02,\
sd.bi = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot09
```

#### 8.2.2.5. Proportion of large error ~ sample size + commingling
```{r}
plot010 <- ggplot(results_df_bi[results_df_bi$v == 0.02, ], aes(x = n, y = c, fill = prop_large_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_prop_large_error_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Proportion of\
Large Errors\
(sd.bi = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot010
```

### 8.2.1. Variation = 0.08
#### 8.2.3.1. Mean error ~ sample size + commingling
```{r}

plot011 <- ggplot(results_df_bi[results_df_bi$v == 0.08, ], aes(x = n, y = c, fill = mean_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  color_scale_mean_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Mean Errors\
(sd.bi = 0.08)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot011
```

#### 8.2.3.2. Median absolute error ~ sample size + commingling
```{r}
plot012 <- ggplot(results_df_bi[results_df_bi$v == 0.08, ], aes(x = n, y = c, fill = median_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_median_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Median Errors\
(sd.bi = 0.08)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot012
```

#### 8.2.3.3. Error 75%  ~ sample size + commingling
```{r}
plot013 <- ggplot(results_df_bi[results_df_bi$v == 0.08, ], aes(x = n, y = c, fill = percentile_75)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_percentile_75_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "75th Percentile\
(sd.bi = 0.08)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot013      
```

#### 8.2.3.4. Large error count ~ sample size + commingling
```{r}
plot014 <- ggplot(results_df_bi[results_df_bi$v == 0.08, ], aes(x = n, y = c, fill = abs_error_count)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_no_large_error_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "The Number of\
Large Error (> 0.02,\
sd.bi = 0.08)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot014

```

#### 8.2.3.5. Proportion of large error ~ sample size + commingling
```{r}
plot015 <- ggplot(results_df_bi[results_df_bi$v == 0.08, ], aes(x = n, y = c, fill = prop_large_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_prop_large_error_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Proportion of\
Large Errors\
(sd.bi = 0.08)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot015
```

## 8.3. Plot CI
### 8.3.1. Variation = 0.01
#### 8.3.1.1. Mean error ~ sample size + commingling
```{r}

plot1 <- ggplot(results_df_ci[results_df_ci$v == 0.01, ], aes(x = n, y = c, fill = mean_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  color_scale_mean_ci +
  xlab('Sample Size') +
  ylab('Commingling degree') +
  labs(fill = "Mean Errors\
(sd.ci = 0.01)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot1
```

#### 8.3.1.2. Median absolute error ~ sample size + commingling
```{r}
plot2 <- ggplot(results_df_ci[results_df_ci$v == 0.01, ], aes(x = n, y = c, fill = median_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_median_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Median Errors\
(sd.ci = 0.01)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot2
```

#### 8.3.1.3. Error 75%  ~ sample size + commingling
```{r}
plot3 <- ggplot(results_df_ci[results_df_ci$v == 0.01, ], aes(x = n, y = c, fill = percentile_75)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_percentile_75_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "75th Percentile 
(sd.ci = 0.01)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot3
```

#### 8.3.1.4. Large error count ~ sample size + commingling
```{r}
plot4 <- ggplot(results_df_ci[results_df_ci$v == 0.01, ], aes(x = n, y = c, fill = abs_error_count)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_no_large_error_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "The Number of\
Large Errors(> 0.02,\
sd.ci = 0.01)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot4
```

#### 8.3.1.5. Proportion of large error ~ sample size + commingling
```{r}
plot5 <- ggplot(results_df_ci[results_df_ci$v == 0.01, ], aes(x = n, y = c, fill = prop_large_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_prop_large_error_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Proportion of\
Large Errors\
(sd.ci = 0.01)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot5
```

### 8.3.2. Variation = 0.02
#### 8.3.2.1. Mean error ~ sample size + commingling
```{r}

plot6 <- ggplot(results_df_ci[results_df_ci$v == 0.02, ], aes(x = n, y = c, fill = mean_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  color_scale_mean_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Mean Errors\
(sd.ci = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot6
```

#### 8.3.2.2. Median absolute error ~ sample size + commingling
```{r}
plot7 <- ggplot(results_df_ci[results_df_ci$v == 0.02, ], aes(x = n, y = c, fill = median_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_median_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Median Errors\
(sd.ci = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot7
```

#### 8.3.2.3. Error 75%  ~ sample size + commingling
```{r}
plot8 <- ggplot(results_df_ci[results_df_ci$v == 0.02, ], aes(x = n, y = c, fill = percentile_75)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_percentile_75_ci+
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "75th Percentile\
(sd.ci = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot8
```

#### 8.3.2.4. Large error count ~ sample size + commingling
```{r}
plot9 <- ggplot(results_df_ci[results_df_ci$v == 0.02, ], aes(x = n, y = c, fill = abs_error_count)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_no_large_error_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "The Number of\
Large Error (> 0.02,\
sd.ci = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot9
```

#### 8.3.2.5. Proportion of large error ~ sample size + commingling
```{r}
plot10 <- ggplot(results_df_ci[results_df_ci$v == 0.02, ], aes(x = n, y = c, fill = prop_large_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_prop_large_error_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Proportion of\
Large Errors\
(sd.ci = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot10
```

### 8.3.3. Variation = 0.05
#### 8.3.3.1. Mean error ~ sample size + commingling
```{r}

plot11 <- ggplot(results_df_ci[results_df_ci$v == 0.05, ], aes(x = n, y = c, fill = mean_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  color_scale_mean_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Mean Errors\
(sd.ci = 0.05)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot11
```

#### 8.3.3.2. Median absolute error ~ sample size + commingling
```{r}
plot12 <- ggplot(results_df_ci[results_df_ci$v == 0.05, ], aes(x = n, y = c, fill = median_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_median_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Median Errors\
(sd.ci = 0.05)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot12
```

#### 8.3.3.3. Error 75%  ~ sample size + commingling
```{r}
plot13 <- ggplot(results_df_ci[results_df_ci$v == 0.05, ], aes(x = n, y = c, fill = percentile_75)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_percentile_75_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "75th Percentile\
(sd.ci = 0.05)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot13
```

#### 8.3.3.4. Large error count ~ sample size + commingling
```{r}
plot14 <- ggplot(results_df_ci[results_df_ci$v == 0.05, ], aes(x = n, y = c, fill = abs_error_count)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_no_large_error_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "The Number of\
Large Error (> 0.02,\
sd.ci = 0.05)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot14
```

#### 8.3.3.5. Proportion of large error ~ sample size + commingling
```{r}
plot15 <- ggplot(results_df_ci[results_df_ci$v == 0.05, ], aes(x = n, y = c, fill = prop_large_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_prop_large_error_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Proportion of\
Large Errors\
(sd.ci = 0.05)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot15
```

## 8.4. Combine the plots
### 8.4.1. Combine the BI plots
```{r}
# Combine the plots using grid.arrange
comb_bi <- grid.arrange(plot01, plot06, plot011,
                        plot02, plot07, plot012,
                        plot03, plot08, plot013, ncol = 3)
```

### 8.4.2. Combine the CI plots
```{r}
# Combine the plots using grid.arrange
comb_ci <- grid.arrange(plot1, plot6, plot11,
                        plot2, plot7, plot12,
                        plot3, plot8, plot13, ncol = 3)
```

### 8.4.2. Combine the BI and CI plots
```{r}
# Combine the plots using grid.arrange
comb_bc <- grid.arrange(plot05, plot5,
                        plot010,plot10,
                        plot015,plot15, ncol = 2)
```





