---
title: "plot_errors"
author: "Doudou Carol Cao"
date: "2023-06-14"
output: html_document
---
# 8. Plot
## 8.1. Set the parameter for indicative lines and common colour scale for each graph
```{r}
# parameter for indicative lines
simulated_n <- c (30, 50, 100)
simulated_c <- c (0.25, 0.5, 0.75)

# Find the common color scale limits for different sets of plots (mean, median, 75 percentile, and the number as well as proportion of large errors)
## BI
color_scale_mean_bi <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_bi$mean_abs_error), max(results_df_bi$mean_abs_error)))
color_scale_median_bi <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_bi$median_abs_error), max(results_df_bi$median_abs_error)))
color_scale_percentile_75_bi <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_bi$percentile_75), max(results_df_bi$percentile_75)))
color_scale_no_large_error_bi <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_bi$abs_error_count), max(results_df_bi$abs_error_count)))
color_scale_prop_large_error_bi <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_bi$prop_large_error), max(results_df_bi$prop_large_error)))

## CI
color_scale_mean_ci <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_ci$mean_abs_error), max(results_df_ci$mean_abs_error)))
color_scale_median_ci <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_ci$median_abs_error), max(results_df_ci$median_abs_error)))
color_scale_percentile_75_ci <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_ci$percentile_75), max(results_df_ci$percentile_75)))
color_scale_no_large_error_ci <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_ci$abs_error_count), max(results_df_ci$abs_error_count)))
color_scale_prop_large_error_ci <- scale_fill_distiller(palette = "RdYlBu", limits = c(min(results_df_ci$prop_large_error), max(results_df_ci$prop_large_error)))
```

## 8.2. Plot-BI
### 8.2.1.Variation = 0.01
#### 8.2.1.1. Mean error ~ sample size + commingling
```{r}
plot01 <- ggplot(results_df_bi[results_df_bi$v == 0.01, ], aes(x = n, y = c, fill = mean_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  color_scale_mean_bi +
  xlab('Sample Size') +
  ylab('Commingling degree') +
  labs(fill = "Mean Errors\
(sd.bi = 0.01)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot01
```

#### 8.2.1.2. Median absolute error ~ sample size + commingling
```{r}
plot02 <- ggplot(results_df_bi[results_df_bi$v == 0.01, ], aes(x = n, y = c, fill = median_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_median_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Median Errors\
(sd.bi = 0.01)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot02
```

#### 8.2.1.3. Error 75%  ~ sample size + commingling
```{r}
plot03 <- ggplot(results_df_bi[results_df_bi$v == 0.01, ], aes(x = n, y = c, fill = percentile_75)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_percentile_75_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "75th Percentile\
(sd.bi = 0.01)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot03
```

#### 8.2.1.4.  Large error count ~ sample size + commingling
```{r}
plot04 <- ggplot(results_df_bi[results_df_bi$v == 0.01, ], aes(x = n, y = c, fill = abs_error_count)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_no_large_error_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "The Number of\
Large Errors(> 0.02,\
sd.bi = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot04
```

#### 8.2.1.5.  Proportion of large error ~ sample size + commingling
```{r}
plot05 <- ggplot(results_df_bi[results_df_bi$v == 0.01, ], aes(x = n, y = c, fill = prop_large_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_prop_large_error_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Proportion of\
Large Errors\
(sd.bi = 0.01)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))
# Print
plot05
```

### 8.2.2. Variation = 0.02
#### 8.2.2.1. Mean error ~ sample size + commingling
```{r}
plot06 <- ggplot(results_df_bi[results_df_bi$v == 0.02, ], aes(x = n, y = c, fill = mean_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  color_scale_mean_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Mean Errors\
(sd.bi = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot06
```

#### 8.2.2.2. Median absolute error ~ sample size + commingling
```{r}
plot07 <- ggplot(results_df_bi[results_df_bi$v == 0.02, ], aes(x = n, y = c, fill = median_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_median_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Median Errors\
(sd.bi = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot07
```

#### 8.2.2.3. Error 75%  ~ sample size + commingling
```{r}
plot08 <- ggplot(results_df_bi[results_df_bi$v == 0.02, ], aes(x = n, y = c, fill = percentile_75)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_percentile_75_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "75th Percentile\
(sd.bi = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot08     
```

#### 8.2.2.4. Large error count ~ sample size + commingling
```{r}
plot09 <- ggplot(results_df_bi[results_df_bi$v == 0.02, ], aes(x = n, y = c, fill = abs_error_count)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_no_large_error_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "The Number of\
Large Error (> 0.02,\
sd.bi = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot09
```

#### 8.2.2.5. Proportion of large error ~ sample size + commingling
```{r}
plot010 <- ggplot(results_df_bi[results_df_bi$v == 0.02, ], aes(x = n, y = c, fill = prop_large_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_prop_large_error_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Proportion of\
Large Errors\
(sd.bi = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot010
```

### 8.2.1. Variation = 0.08
#### 8.2.3.1. Mean error ~ sample size + commingling
```{r}

plot011 <- ggplot(results_df_bi[results_df_bi$v == 0.08, ], aes(x = n, y = c, fill = mean_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  color_scale_mean_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Mean Errors\
(sd.bi = 0.08)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot011
```

#### 8.2.3.2. Median absolute error ~ sample size + commingling
```{r}
plot012 <- ggplot(results_df_bi[results_df_bi$v == 0.08, ], aes(x = n, y = c, fill = median_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_median_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Median Errors\
(sd.bi = 0.08)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot012
```

#### 8.2.3.3. Error 75%  ~ sample size + commingling
```{r}
plot013 <- ggplot(results_df_bi[results_df_bi$v == 0.08, ], aes(x = n, y = c, fill = percentile_75)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_percentile_75_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "75th Percentile\
(sd.bi = 0.08)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot013      
```

#### 8.2.3.4. Large error count ~ sample size + commingling
```{r}
plot014 <- ggplot(results_df_bi[results_df_bi$v == 0.08, ], aes(x = n, y = c, fill = abs_error_count)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_no_large_error_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "The Number of\
Large Error (> 0.02,\
sd.bi = 0.08)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot014

```

#### 8.2.3.5. Proportion of large error ~ sample size + commingling
```{r}
plot015 <- ggplot(results_df_bi[results_df_bi$v == 0.08, ], aes(x = n, y = c, fill = prop_large_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_prop_large_error_bi +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Proportion of\
Large Errors\
(sd.bi = 0.08)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot015
```

## 8.3. Plot CI
### 8.3.1. Variation = 0.01
#### 8.3.1.1. Mean error ~ sample size + commingling
```{r}

plot1 <- ggplot(results_df_ci[results_df_ci$v == 0.01, ], aes(x = n, y = c, fill = mean_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  color_scale_mean_ci +
  xlab('Sample Size') +
  ylab('Commingling degree') +
  labs(fill = "Mean Errors\
(sd.ci = 0.01)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot1
```

#### 8.3.1.2. Median absolute error ~ sample size + commingling
```{r}
plot2 <- ggplot(results_df_ci[results_df_ci$v == 0.01, ], aes(x = n, y = c, fill = median_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_median_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Median Errors\
(sd.ci = 0.01)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot2
```

#### 8.3.1.3. Error 75%  ~ sample size + commingling
```{r}
plot3 <- ggplot(results_df_ci[results_df_ci$v == 0.01, ], aes(x = n, y = c, fill = percentile_75)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_percentile_75_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "75th Percentile 
(sd.ci = 0.01)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot3
```

#### 8.3.1.4. Large error count ~ sample size + commingling
```{r}
plot4 <- ggplot(results_df_ci[results_df_ci$v == 0.01, ], aes(x = n, y = c, fill = abs_error_count)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_no_large_error_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "The Number of\
Large Errors(> 0.02,\
sd.ci = 0.01)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot4
```

#### 8.3.1.5. Proportion of large error ~ sample size + commingling
```{r}
plot5 <- ggplot(results_df_ci[results_df_ci$v == 0.01, ], aes(x = n, y = c, fill = prop_large_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_prop_large_error_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Proportion of\
Large Errors\
(sd.ci = 0.01)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot5
```

### 8.3.2. Variation = 0.02
#### 8.3.2.1. Mean error ~ sample size + commingling
```{r}

plot6 <- ggplot(results_df_ci[results_df_ci$v == 0.02, ], aes(x = n, y = c, fill = mean_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  color_scale_mean_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Mean Errors\
(sd.ci = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot6
```

#### 8.3.2.2. Median absolute error ~ sample size + commingling
```{r}
plot7 <- ggplot(results_df_ci[results_df_ci$v == 0.02, ], aes(x = n, y = c, fill = median_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_median_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Median Errors\
(sd.ci = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot7
```

#### 8.3.2.3. Error 75%  ~ sample size + commingling
```{r}
plot8 <- ggplot(results_df_ci[results_df_ci$v == 0.02, ], aes(x = n, y = c, fill = percentile_75)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_percentile_75_ci+
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "75th Percentile\
(sd.ci = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot8
```

#### 8.3.2.4. Large error count ~ sample size + commingling
```{r}
plot9 <- ggplot(results_df_ci[results_df_ci$v == 0.02, ], aes(x = n, y = c, fill = abs_error_count)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_no_large_error_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "The Number of\
Large Error (> 0.02,\
sd.ci = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot9
```

#### 8.3.2.5. Proportion of large error ~ sample size + commingling
```{r}
plot10 <- ggplot(results_df_ci[results_df_ci$v == 0.02, ], aes(x = n, y = c, fill = prop_large_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_prop_large_error_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Proportion of\
Large Errors\
(sd.ci = 0.02)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot10
```

### 8.3.3. Variation = 0.05
#### 8.3.3.1. Mean error ~ sample size + commingling
```{r}

plot11 <- ggplot(results_df_ci[results_df_ci$v == 0.05, ], aes(x = n, y = c, fill = mean_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', linewidth = 0.5, linetype = 'dashed') +
  color_scale_mean_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Mean Errors\
(sd.ci = 0.05)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot11
```

#### 8.3.3.2. Median absolute error ~ sample size + commingling
```{r}
plot12 <- ggplot(results_df_ci[results_df_ci$v == 0.05, ], aes(x = n, y = c, fill = median_abs_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_median_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Median Errors\
(sd.ci = 0.05)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot12
```

#### 8.3.3.3. Error 75%  ~ sample size + commingling
```{r}
plot13 <- ggplot(results_df_ci[results_df_ci$v == 0.05, ], aes(x = n, y = c, fill = percentile_75)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_percentile_75_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "75th Percentile\
(sd.ci = 0.05)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot13
```

#### 8.3.3.4. Large error count ~ sample size + commingling
```{r}
plot14 <- ggplot(results_df_ci[results_df_ci$v == 0.05, ], aes(x = n, y = c, fill = abs_error_count)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_no_large_error_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "The Number of\
Large Error (> 0.02,\
sd.ci = 0.05)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot14
```

#### 8.3.3.5. Proportion of large error ~ sample size + commingling
```{r}
plot15 <- ggplot(results_df_ci[results_df_ci$v == 0.05, ], aes(x = n, y = c, fill = prop_large_error)) +
  geom_raster() +
  geom_vline(xintercept = simulated_n, color = 'black', size = 0.5, linetype = 'dashed') +
  geom_hline(yintercept = simulated_c, color = 'black', size = 0.5, linetype = 'dashed') +
  color_scale_prop_large_error_ci +
  xlab('Sample Size') +
  ylab('Commingling') +
  labs(fill = "Proportion of\
Large Errors\
(sd.ci = 0.05)") +
  coord_cartesian(expand = FALSE) +
  theme_bw() +
  theme(panel.grid = element_blank(), panel.border = element_blank(),
        axis.text = element_text(size = 8, face = 'bold'),  # Adjust axis text size
        axis.title = element_text(size = 8, face = 'bold'), # Adjust axis title size
        legend.title = element_text(size = 8, face = 'bold'),
        legend.text = element_text(size = 8, face = 'bold'))

# Print
plot15
```

## 8.4. Combine the plots
### 8.4.1. Combine the BI plots
```{r}
# Combine the plots using grid.arrange
comb_bi <- grid.arrange(plot01, plot06, plot011,
                        plot02, plot07, plot012,
                        plot03, plot08, plot013, ncol = 3)
```

### 8.4.2. Combine the CI plots
```{r}
# Combine the plots using grid.arrange
comb_ci <- grid.arrange(plot1, plot6, plot11,
                        plot2, plot7, plot12,
                        plot3, plot8, plot13, ncol = 3)
```

### 8.4.2. Combine the BI and CI plots
```{r}
# Combine the plots using grid.arrange
comb_bc <- grid.arrange(plot05, plot5,
                        plot010,plot10,
                        plot015,plot15, ncol = 2)
```
