---
title: "Prepare_summary_and_compare_data"
author: "Doudou Carol Cao"
date: "2023-06-14"
output: html_document
---
# Install and load necessary packages
```{r}
install.packages("tidyverse", repos = "https://cran.r-project.org/")
install.packages("viridis", repos = "https://cran.r-project.org/")
install.packages("terra", repos = "https://cran.r-project.org/")
install.packages("gridExtra", repos = "https://cran.r-project.org/") 

library(viridis)
library(tidyverse)
library(terra)
library(gridExtra)
library(scales)
library(readxl)
library(httr)

```

# 1. Prepare the data
## 1.1. Read the Goldman and EU datasets
```{r}
# Goldman dataset
GET('http://web.utk.edu/~auerbach/Goldman.xls', write_disk(tf_gm <- tempfile(fileext = ".xls")))
Goldman <- read_excel(tf_gm)
# Save Goldman dataset as a CSV file in user-defined path
write.csv(Goldman, file = "path/to/Goldman.csv", row.names = FALSE)
# Read Goldman dataset as CSV
Goldman <- read.csv("path/to/Goldman.csv")

# EU_Ruff
GET('https://fae.johnshopkins.edu/wp-content/uploads/2022/08/European-Data-Set-7-22.xlsx', write_disk(tf_eu <- tempfile(fileext = ".xls")))
EU <- read_excel(tf_eu)
# Save EU_Ruff dataset as a CSV file
write.csv(EU, file = "path/to/EU_Ruff.csv", row.names = FALSE)
# Read EU_Ruff dataset as CSV
EU <- read.csv("path/to/EU_Ruff.csv")
```

## 1.2. Select the columns of interest (Assuming datasets have been loaded)
```{r}
# Select limb lengths in Goldman dataset
Goldman_selected_columns <- Goldman[, c("ID", "Sex", "NOTE", "LHML", "RHML", "LRML", "RRML", "LFBL", "RFBL", "LTML", "RTML")]

# Select limb lengths in EU_Ruff dataset
EU_selected_columns <- EU[, c("SITE", "SPECIMEN_No", "SEX", "DATE.RANGE", "YEARS.BP", "FBICLN", "TMAXLN", "HRMAXLN", "HLMAXLN", "RRMAXLN", "RLMAXLN")]
```

## 1.3. Calculate final length of the humerus (HML), radius (RML),femur (FBL) and tibia (TML)\
---Because in some limbs, the lengths of both left and right sides are reported, the final length of a limb is the averge of two sides-
```{r}
# --- Arm ---
## Goldman
### Average the maximum length of the left and right humerus 
Goldman_selected_columns$finalHML <- rowMeans(Goldman_selected_columns[, c("LHML", "RHML")], na.rm = TRUE)

### Average the maximum length of the left and right radius 
Goldman_selected_columns$finalRML <- rowMeans(Goldman_selected_columns[, c("LRML", "RRML")], na.rm = TRUE)

## EU_Ruff
### Average the maximum length of the left and right humerus 
EU_selected_columns$finalHML <- rowMeans(EU_selected_columns[, c("HRMAXLN", "HLMAXLN")], na.rm = TRUE)

### Average the maximum length of the left and right radius 
EU_selected_columns$finalRML <- rowMeans(EU_selected_columns[, c("RRMAXLN", "RLMAXLN")], na.rm = TRUE)

# --- Leg ---

## Goldman
### Average the bicondylar length of the left and right femur
Goldman_selected_columns$finalFBL <- rowMeans(Goldman_selected_columns[, c("LFBL", "RFBL")], na.rm = TRUE)

### Average the maximum length of the left and right tibia 
Goldman_selected_columns$finalTML <- rowMeans(Goldman_selected_columns[, c("LTML", "RTML")], na.rm = TRUE)
```

## 1.4. Drop rows with missing values
```{r}
# --- Arm ---
Goldman_filtered_arm <- Goldman_selected_columns[complete.cases(Goldman_selected_columns$finalHML, Goldman_selected_columns$finalRML), ]

## EU_Ruff
EU_filtered_arm <- EU_selected_columns[complete.cases(EU_selected_columns$finalHML, EU_selected_columns$finalRML), ]

# --- Leg ---
## Goldman 
Goldman_filtered_leg <- Goldman_selected_columns[complete.cases(Goldman_selected_columns$finalFBL, Goldman_selected_columns$finalTML), ]

## EU_Ruff
EU_filtered_leg <- EU_selected_columns[complete.cases(EU_selected_columns$TMAXLN, EU_selected_columns$FBICLN), ]
```

## 1.5. Filter out small-size groups (no.individuals < 5)

```{r}
# Count number of individuals per NOTE (in Goldman dataset) and SITE group (in EU_Ruff set)
# Arm
no_group_GM_arm <- table(Goldman_filtered_arm$NOTE)
no_group_EU_arm <- table(EU_filtered_arm$SITE)

# Leg
no_group_GM_leg <- table(Goldman_filtered_leg$NOTE)
no_group_EU_leg <- table(EU_filtered_leg$SITE)

# Filter out small-size groups (no.individuals < 5)
## Arm
### Goldman
Goldman_filtered_final_arm <- Goldman_filtered_arm[Goldman_filtered_arm$NOTE %in% names(no_group_GM_arm[no_group_GM_arm >= 5]), ]

### EU_Ruff
EU_filtered_final_arm <- EU_filtered_arm[EU_filtered_arm$SITE %in% names(no_group_EU_arm[no_group_EU_arm >= 5]), ]

## Leg
### Goldman
Goldman_filtered_final_leg <- Goldman_filtered_leg[Goldman_filtered_leg$NOTE %in% names(no_group_GM_leg[no_group_GM_leg >= 5]), ]

EU_filtered_final_leg <- EU_filtered_leg[EU_filtered_leg$SITE %in% names(no_group_EU_leg[no_group_EU_leg >= 5]), ]
```

## 1.6. Calculate the Conventional Brachial and Crural indices

```{r}

# Brachial index
## Goldman
Goldman_filtered_final_arm$ConventionalBI <- Goldman_filtered_final_arm$finalRML/ 
Goldman_filtered_final_arm$finalHML

## EU_Ruff
EU_filtered_final_arm$ConventionalBI <- EU_filtered_final_arm$finalRML/ 
EU_filtered_final_arm$finalHML

# Crural index
## Goldman
Goldman_filtered_final_leg$ConventionalCI <- Goldman_filtered_final_leg$finalTML / 
Goldman_filtered_final_leg$finalFBL

# Rename columns
names(EU_filtered_final_leg)[names(EU_filtered_final_leg) == "FBICLN"] <- "finalFBL"
names(EU_filtered_final_leg)[names(EU_filtered_final_leg) == "TMAXLN"] <- "finalTML"

# Calculate TrueCI
EU_filtered_final_leg$ConventionalCI <- EU_filtered_final_leg$finalTML / EU_filtered_final_leg$finalFBL
```


# 2. Create the subset of the arm and leg

## 2.1. Data cleaning and transformation operations on the Sex column of two datasets
```{r}
# Convert missing data or uncertain sex values to NA in arm dataset
Goldman_filtered_final_arm$Sex <- ifelse(Goldman_filtered_final_arm$Sex %in% c("0?", "1?"), NA, Goldman_filtered_final_arm$Sex)

# Convert 0 and 1 values to 1 and 2, respectively, in arm dataset
Goldman_filtered_final_arm$Sex <- ifelse(Goldman_filtered_final_arm$Sex == 1, 2, Goldman_filtered_final_arm$Sex)
Goldman_filtered_final_arm$Sex <- ifelse(Goldman_filtered_final_arm$Sex == 0, 1, Goldman_filtered_final_arm$Sex)

# Convert missing data or uncertain sex values to NA in leg dataset
Goldman_filtered_final_leg$Sex <- ifelse(Goldman_filtered_final_leg$Sex %in% c("0?", "1?"), NA, Goldman_filtered_final_leg$Sex)

# Convert 0 and 1 values to 1 and 2, respectively, in leg dataset
Goldman_filtered_final_leg$Sex <- ifelse(Goldman_filtered_final_leg$Sex == 1, 2, Goldman_filtered_final_leg$Sex)
Goldman_filtered_final_leg$Sex <- ifelse(Goldman_filtered_final_leg$Sex == 0, 1, Goldman_filtered_final_leg$Sex)
```

## 2.2. Create the subset of the arm and leg
```{r}
Armset <- rbind(transform(
    EU_filtered_final_arm[, c("SITE", "SEX", "SPECIMEN_No", "finalHML", "finalRML", "ConventionalBI")],
    ID = SPECIMEN_No,
    Sex = SEX,
    source = "EU"
  )[, c("SITE", "ID", "Sex", "finalHML", "finalRML", "ConventionalBI")]
,
transform(
    Goldman_filtered_final_arm[, c("NOTE", "ID", "Sex", "finalHML", "finalRML", "ConventionalBI")],
    SITE = NOTE,
    source = "Goldman"
    )[, c("SITE", "ID", "Sex", "finalHML", "finalRML", "ConventionalBI")]
  
)

# Legset
Legset <- rbind(
  transform(
    EU_filtered_final_leg[, c("SITE", "SEX", "SPECIMEN_No", "finalFBL", "finalTML", "ConventionalCI")],
    ID = SPECIMEN_No,
    Sex = SEX,
    source = "EU"
  )[, c("SITE", "Sex", "ID", "finalFBL", "finalTML", "ConventionalCI")],
  transform(
    Goldman_filtered_final_leg[, c("NOTE", "ID", "Sex", "finalTML", "finalFBL", "ConventionalCI")],
    SITE = NOTE,
    source = "Goldman",
    Sex = as.numeric(Sex)
  )[, c("SITE", "Sex", "ID", "finalFBL", "finalTML", "ConventionalCI")]
)
```

# 3. Visualise the limb lengths and indices between males and females
## 3.1. Counting males and females 
```{r}
# Counting males and females in Armset dataset
Armset_count_male <- sum(Armset$Sex == 1, na.rm = TRUE)
Armset_count_female <- sum(Armset$Sex == 2, na.rm = TRUE)

# Counting males and females  in Legset dataset
Legset_count_male  <- sum(Legset$Sex == 1, na.rm = TRUE)
Legset_count_female <- sum(Legset$Sex == 2, na.rm = TRUE)

# Print the counts
cat("Count of males in Armset:", Armset_count_male, "\n")
cat("Count of females in Armset:", Armset_count_female, "\n")
cat("Count of males in Legset:", Legset_count_male, "\n")
cat("Count of females in Legset:", Legset_count_female, "\n")
```

## 3.2. Plot the lengths and indices of males and females 
### 3.2.1 Combine the data
```{r}
# Combine the data of limb lengths
HML_male <- Armset$finalHML[Armset$Sex == 1]
HML_female <- Armset$finalHML[Armset$Sex == 2]
HML_both <- Armset$finalHML
RML_male <- Armset$finalRML[Armset$Sex == 1]
RML_female <- Armset$finalRML[Armset$Sex == 2]
RML_both <- Armset$finalRML
FBL_male <- Legset$finalFBL[Legset$Sex == 1]
FBL_female <- Legset$finalFBL[Legset$Sex == 2]
FBL_both <- Legset$finalFBL
TML_male <- Legset$finalTML[Legset$Sex == 1]
TML_female <- Legset$finalTML[Legset$Sex == 2]
TML_both <- Legset$finalTML

# Combine the data of index
BI_male <- Armset$ConventionalBI[Armset$Sex == 1]
BI_female <- Armset$ConventionalBI[Armset$Sex == 2]
BI_both <- Armset$ConventionalBI
CI_male <- Legset$ConventionalCI[Legset$Sex == 1]
CI_female <- Legset$ConventionalCI[Legset$Sex == 2]
CI_both <- Legset$ConventionalCI
```

```{r}

# Create a data frame for HML
df_HML <- data.frame(values = c(HML_male, HML_female),
                 group = rep(c("HML - Male", "HML - Female"), c(length(HML_male), length(HML_female))))

# Create the histogram for HML 
p1 <- ggplot(df_HML, aes(x = values, fill = group)) + 
  geom_histogram(binwidth = 10, alpha = 0.6, position = "identity") +
  scale_fill_manual(values = c("#d45087","skyblue" )) +
  labs(title = "", x = "HML", y = "Frequency", fill = "Sex") +
  theme_classic()+
  theme(legend.title = element_text(face = "bold", size = 12),
        legend.text = element_text(face = "bold", size = 12),
        axis.title = element_text(face = "bold", size = 14),
        axis.text =  element_text(face = "bold", size = 12))


# Create a data frame for RML
df_RML <- data.frame(values = c(RML_male, RML_female),
                 group = rep(c("RML - Male", "RML - Female"), c(length(RML_male), length(RML_female))))

# Create the histogram for RML
p2 <- ggplot(df_RML, aes(x = values, fill = group)) + 
  geom_histogram(binwidth = 10, alpha = 0.6, position = "identity") +
  scale_fill_manual(values = c( "#d45087","skyblue" )) +
  labs(title = "", x = "RML", y = "Frequency", fill = "Sex") +
  theme_classic()+
  theme(legend.title = element_text(face = "bold", size = 12),
        legend.text = element_text(face = "bold", size = 12),
        axis.title = element_text(face = "bold", size = 14),
        axis.text =  element_text(face = "bold", size = 12))


# Create a data frame for FBL
df_FBL <- data.frame(values = c(FBL_male, FBL_female),
                 group = rep(c("FBL - Male", "FBL - Female"), c(length(FBL_male), length(FBL_female))))

# Create the histogram for FBL
p3 <- ggplot(df_FBL, aes(x = values, fill = group)) + 
  geom_histogram(binwidth = 10, alpha = 0.6, position = "identity") +
  scale_fill_manual(values = c("#a05195",  "blue")) +
  labs(title = "", x = "FBL", y = "Frequency", fill = "Sex") +
  theme_classic()+
  theme(legend.title = element_text(face = "bold", size = 12),
        legend.text = element_text(face = "bold", size = 12),
        axis.title = element_text(face = "bold", size = 14),
        axis.text =  element_text(face = "bold", size = 12))

# Create a data frame for TML
df_TML <- data.frame(values = c(TML_male, TML_female),
                 group = rep(c("TML - Male", "TML - Female"), c(length(TML_male), length(TML_female))))

# Create a data frame for TML
df_TML <- data.frame(values = c(TML_male, TML_female),
                 group = rep(c("TML - Male", "TML - Female"), c(length(TML_male), length(TML_female))))

# Create the histogram for RML
p4 <- ggplot(df_TML, aes(x = values, fill = group)) + 
  geom_histogram(binwidth = 10, alpha = 0.6, position = "identity") +
  scale_fill_manual(values = c( "#a05195",  "blue")) +
  labs(title = "", x = "TML", y = "Frequency", fill = "Sex") +
  theme_classic()+
  theme(legend.title = element_text(face = "bold", size = 12),
        legend.text = element_text(face = "bold", size = 12),
        axis.title = element_text(face = "bold", size = 14),
        axis.text =  element_text(face = "bold", size = 12))

# Create a data frame for BI
df_BI <- subset(data.frame(values = c(BI_male, BI_female),
                 group = rep(c("BIt - Male", "BIt - Female"), c(length(BI_male), length(BI_female)))),
               values > 0.6 & values < 0.99)

# Create the histogram for BIt 

p5 <- ggplot(df_BI, aes(x = values, fill = group)) + 
  geom_histogram(binwidth = 0.01, alpha = 0.6, position = "identity") +
  scale_fill_manual(values = c("#d45087", "skyblue")) +
  labs(title = "", x = "BIc", y = "Frequency", fill = "Sex") +
  theme_classic() +
  theme(
    legend.title = element_text(face = "bold", size = 14),
    legend.text = element_text(face = "bold", size = 14),
    axis.title = element_text(face = "bold", size = 18),
    axis.text =  element_text(face = "bold", size = 14)) +
    scale_x_continuous(breaks = seq(0, 1, by = 0.05))

# Create a data frame for CI
df_CI <- subset(data.frame(values = c(CI_male, CI_female),
                 group = rep(c("CIt - Male", "CIt - Female"), c(length(CI_male), length(CI_female)))), values < 1)

# Create the histogram for CIt
p6 <- ggplot(df_CI, aes(x = values, fill = group)) + 
  geom_histogram(binwidth = 0.01, alpha = 0.6, position = "identity") +
  scale_fill_manual(values = c( "#a05195",  "blue")) +
  labs(title = "", x = "CIc", y = "Frequency", fill = "Sex") +
  theme_classic()+
  theme(legend.title = element_text(face = "bold", size = 14),
        legend.text = element_text(face = "bold", size = 14),
        axis.title = element_text(face = "bold", size = 18),
        axis.text =  element_text(face = "bold", size = 14))

# Create the combined plot
combined_histogram_limblength <- grid.arrange(p1, p2, p3, p4, ncol = 2,nrow = 2)
combined_histogram_indices <- grid.arrange(p5, p6, ncol = 2)
combined_histogram_limblength_indices <- grid.arrange(p1, p2, p3, p4, p5, p6, ncol = 2)
```

# 4. Summarise the limb lengths and indices
## 4.1. Summarise the limb lengths 
### 4.1.1. Summarise the limb lengths (combined)
```{r}
# Humerus
Mean_HML <- aggregate(Armset$finalHML, by = list(Armset$SITE), FUN = mean)
colnames(Mean_HML) <- c("SITE", "mean_finalHML")

summary_HML <- data.frame(
  mean_mean_finalHML = mean(Mean_HML$mean_finalHML),
  max_mean_finalHML = max(Mean_HML$mean_finalHML),
  min_mean_finalHML = min(Mean_HML$mean_finalHML),
  sd_mean_finalHML = sd(Mean_HML$mean_finalHML)
)

# Radius
Mean_RML <- aggregate(Armset$finalRML, by = list(Armset$SITE), FUN = mean)
colnames(Mean_RML) <- c("SITE", "mean_finalRML")

summary_RML <- data.frame(
  mean_mean_finalRML = mean(Mean_RML$mean_finalRML),
  max_mean_finalRML = max(Mean_RML$mean_finalRML),
  min_mean_finalRML = min(Mean_RML$mean_finalRML),
  sd_mean_finalRML = sd(Mean_RML$mean_finalRML)
)

# Femur
Mean_FBL <- aggregate(Legset$finalFBL, by = list(Legset$SITE), FUN = mean)
colnames(Mean_FBL) <- c("SITE", "mean_finalFBL")

summary_FBL <- data.frame(
  mean_mean_finalFBL = mean(Mean_FBL$mean_finalFBL),
  max_mean_finalFBL = max(Mean_FBL$mean_finalFBL),
  min_mean_finalFBL = min(Mean_FBL$mean_finalFBL),
  sd_mean_finalFBL = sd(Mean_FBL$mean_finalFBL)
)

# Tibia
Mean_TML <- aggregate(Legset$finalTML, by = list(Legset$SITE), FUN = mean)
colnames(Mean_TML) <- c("SITE", "mean_finalTML")

summary_TML <- data.frame(
  mean_mean_finalTML = mean(Mean_TML$mean_finalTML),
  max_mean_finalTML = max(Mean_TML$mean_finalTML),
  min_mean_finalTML = min(Mean_TML$mean_finalTML),
  sd_mean_finalTML = sd(Mean_TML$mean_finalTML)
)

# Print summary statistics
print(summary_HML)
print(summary_RML)
print(summary_FBL)
print(summary_TML)
```

### 4.1.2. Summarise the limb lengths (by sex)
```{r}
# Humerus
## Male
Mean_HML_male <- aggregate(finalHML ~ SITE, data = Armset[Armset$Sex == 1, ], FUN = mean)
colnames(Mean_HML_male) <- c("SITE", "mean_finalHML_male")

summary_HML_male <- data.frame(
  mean_mean_finalHML_male = mean(Mean_HML_male$mean_finalHML_male),
  max_mean_finalHML_male = max(Mean_HML_male$mean_finalHML_male),
  min_mean_finalHML_male = min(Mean_HML_male$mean_finalHML_male),
  sd_mean_finalHML_male = sd(Mean_HML_male$mean_finalHML_male)
)

## Female
Mean_HML_female <- aggregate(finalHML ~ SITE, data = Armset[Armset$Sex == 2, ], FUN = mean)
colnames(Mean_HML_female) <- c("SITE", "mean_finalHML_female")

summary_HML_female <- data.frame(
  mean_mean_finalHML_female = mean(Mean_HML_female$mean_finalHML_female),
  max_mean_finalHML_female = max(Mean_HML_female$mean_finalHML_female),
  min_mean_finalHML_female = min(Mean_HML_female$mean_finalHML_female),
  sd_mean_finalHML_female = sd(Mean_HML_female$mean_finalHML_female)
)

# Radius
## Male
Mean_RML_male <- aggregate(finalRML ~ SITE, data = Armset[Armset$Sex == 1, ], FUN = mean)
colnames(Mean_RML_male) <- c("SITE", "mean_finalRML_male")

summary_RML_male <- data.frame(
  mean_mean_finalRML_male = mean(Mean_RML_male$mean_finalRML_male),
  max_mean_finalRML_male = max(Mean_RML_male$mean_finalRML_male),
  min_mean_finalRML_male = min(Mean_RML_male$mean_finalRML_male),
  sd_mean_finalRML_male = sd(Mean_RML_male$mean_finalRML_male)
)

## Female
Mean_RML_female <- aggregate(finalRML ~ SITE, data = Armset[Armset$Sex == 2, ], FUN = mean)
colnames(Mean_RML_female) <- c("SITE", "mean_finalRML_female")

summary_RML_female <- data.frame(
  mean_mean_finalRML_female = mean(Mean_RML_female$mean_finalRML_female),
  max_mean_finalRML_female = max(Mean_RML_female$mean_finalRML_female),
  min_mean_finalRML_female = min(Mean_RML_female$mean_finalRML_female),
  sd_mean_finalRML_female = sd(Mean_RML_female$mean_finalRML_female)
)

# Femur
## Male
Mean_FBL_male <- aggregate(finalFBL ~ SITE, data = Legset[Legset$Sex == 1, ], FUN = mean)
colnames(Mean_FBL_male) <- c("SITE", "mean_finalFBL_male")

summary_FBL_male <- data.frame(
  mean_mean_finalFBL_male = mean(Mean_FBL_male$mean_finalFBL_male),
  max_mean_finalFBL_male = max(Mean_FBL_male$mean_finalFBL_male),
  min_mean_finalFBL_male = min(Mean_FBL_male$mean_finalFBL_male),
  sd_mean_finalFBL_male = sd(Mean_FBL_male$mean_finalFBL_male)
)

## Female
Mean_FBL_female <- aggregate(finalFBL ~ SITE, data = Legset[Legset$Sex == 2, ], FUN = mean)
colnames(Mean_FBL_female) <- c("SITE", "mean_finalFBL_female")

summary_FBL_female <- data.frame(
  mean_mean_finalFBL_female = mean(Mean_FBL_female$mean_finalFBL_female),
  max_mean_finalFBL_female = max(Mean_FBL_female$mean_finalFBL_female),
  min_mean_finalFBL_female = min(Mean_FBL_female$mean_finalFBL_female),
  sd_mean_finalFBL_female = sd(Mean_FBL_female$mean_finalFBL_female)
)

# Tibia
## Male
Mean_TML_male <- aggregate(finalTML ~ SITE, data = Legset[Legset$Sex == 1, ], FUN = mean)
colnames(Mean_TML_male) <- c("SITE", "mean_finalTML_male")

summary_TML_male <- data.frame(
  mean_mean_finalTML_male = mean(Mean_TML_male$mean_finalTML_male),
  max_mean_finalTML_male = max(Mean_TML_male$mean_finalTML_male),
  min_mean_finalTML_male = min(Mean_TML_male$mean_finalTML_male),
  sd_mean_finalTML_male = sd(Mean_TML_male$mean_finalTML_male)
)

## Female
Mean_TML_female <- aggregate(finalTML ~ SITE, data = Legset[Legset$Sex == 2, ], FUN = mean)
colnames(Mean_TML_female) <- c("SITE", "mean_finalTML_female")

summary_TML_female <- data.frame(
  mean_mean_finalTML_female = mean(Mean_TML_female$mean_finalTML_female),
  max_mean_finalTML_female = max(Mean_TML_female$mean_finalTML_female),
  min_mean_finalTML_female = min(Mean_TML_female$mean_finalTML_female),
  sd_mean_finalTML_female = sd(Mean_TML_female$mean_finalTML_female)
)

# Print summary statistics
summary_HML_male
summary_HML_female
summary_RML_male
summary_RML_female
summary_FBL_male
summary_FBL_female
summary_TML_male
summary_TML_female
```

## 4.2 Summarise the indices
### 4.2.1. Summarise the indices (combined)
```{r}
# Brachial index
## Mean_BIc
Mean_BIc <- aggregate(Armset$ConventionalBI, by = list(Armset$SITE), FUN = mean)
colnames(Mean_BIc) <- c("SITE", "mean_BIc")

summary_mean_BIc <- data.frame(
  mean_mean_BIc = mean(Mean_BIc$mean_BIc),
  max_mean_BIc = max(Mean_BIc$mean_BIc),
  min_mean_BIc = min(Mean_BIc$mean_BIc),
  sd_mean_BIc = sd(Mean_BIc$mean_BIc)
)

## SD_BIc
SD_BIc <- aggregate(Armset$ConventionalBI, by = list(Armset$SITE), FUN = sd)
colnames(SD_BIc) <- c("SITE", "sd_BIc")

summary_sd_BIc <- data.frame(
  mean_sd_BIc = mean(SD_BIc$sd_BIc),
  max_sd_BIc = max(SD_BIc$sd_BIc),
  min_sd_BIc = min(SD_BIc$sd_BIc),
  sd_sd_BIc = sd(SD_BIc$sd_BIc)
)


# Crural index
## Mean_CIt
Mean_CIc <- aggregate(Legset$ConventionalCI, by = list(Legset$SITE), FUN = mean)
colnames(Mean_CIc) <- c("SITE", "mean_CIc")

summary_mean_CIc <- data.frame(
  mean_mean_CIc = mean(Mean_CIc$mean_CIc),
  max_mean_CIc = max(Mean_CIc$mean_CIc),
  min_mean_CIc = min(Mean_CIc$mean_CIc),
  sd_mean_CIc = sd(Mean_CIc$mean_CIc)
)

## SD_CIt
SD_CIc <- aggregate(Legset$ConventionalCI, by = list(Legset$SITE), FUN = sd)
colnames(SD_CIc) <- c("SITE", "sd_CIc")

summary_sd_CIc <- data.frame(
  mean_sd_CIc = mean(SD_CIc$sd_CIc),
  max_sd_CIc = max(SD_CIc$sd_CIc),
  min_sd_CIc = min(SD_CIc$sd_CIc),
  sd_sd_CIc = sd(SD_CIc$sd_CIc)
)

# Print summary statistics
summary_mean_BIc
summary_mean_CIc
summary_sd_BIc
summary_sd_CIc
```

### 4.2.2. Summarise the indices (by sex)
```{r}

# Brachial index
## Mean_BIc 
### Male
Mean_BIc_male <- aggregate(ConventionalBI ~ SITE, data = Armset[Armset$Sex == 1, ], FUN = mean)
colnames(Mean_BIc_male) <- c("SITE", "mean_BIc_male")

summary_mean_BIc_male <- data.frame(
  mean_mean_BIc_male = mean(Mean_BIc_male$mean_BIc_male),
  max_mean_BIc_male = max(Mean_BIc_male$mean_BIc_male),
  min_mean_BIc_male = min(Mean_BIc_male$mean_BIc_male),
  sd_mean_BIc_male = sd(Mean_BIc_male$mean_BIc_male)
)

## SD_BIc 
### Male
SD_BIc_male <- aggregate(ConventionalBI ~ SITE, data = Armset[Armset$Sex == 1, ], FUN = sd)
colnames(SD_BIc_male) <- c("SITE", "sd_BIc_male")

summary_sd_BIc_male <- data.frame(
  mean_sd_BIc_male = mean(SD_BIc_male$sd_BIc_male, na.rm = TRUE),
  max_sd_BIc_male = max(SD_BIc_male$sd_BIc_male, na.rm = TRUE),
  min_sd_BIc_male = min(SD_BIc_male$sd_BIc_male, na.rm = TRUE),
  sd_sd_BIc_male = sd(SD_BIc_male$sd_BIc_male, na.rm = TRUE)
)

#### Female
Mean_BIc_female <- aggregate(ConventionalBI ~ SITE, data = Armset[Armset$Sex == 2, ], FUN = mean)
colnames(Mean_BIc_female) <- c("SITE", "mean_BIc_female")

summary_mean_BIc_female <- data.frame(
  mean_mean_BIc_female = mean(Mean_BIc_female$mean_BIc_female),
  max_mean_BIc_female = max(Mean_BIc_female$mean_BIc_female),
  min_mean_BIc_female = min(Mean_BIc_female$mean_BIc_female),
  sd_mean_BIc_female = sd(Mean_BIc_female$mean_BIc_female)
)

### SD_BIt 
SD_BIc_female <- aggregate(ConventionalBI ~ SITE, data = Armset[Armset$Sex == 2, ], FUN = sd)
colnames(SD_BIc_female) <- c("SITE", "sd_BIc_female")

summary_sd_BIc_female <- data.frame(
  mean_sd_BIc_female = mean(SD_BIc_female$sd_BIc_female, na.rm = TRUE),
  max_sd_BIc_female = max(SD_BIc_female$sd_BIc_female, na.rm = TRUE),
  min_sd_BIc_female = min(SD_BIc_female$sd_BIc_female, na.rm = TRUE),
  sd_sd_BIc_female = sd(SD_BIc_female$sd_BIc_female, na.rm = TRUE)
)

## Crural index

### Male
#### Mean_CIc
Mean_CIc_male <- aggregate(Legset$ConventionalCI[Legset$Sex == 1], by = list(Legset$SITE[Legset$Sex == 1]), FUN = mean)
colnames(Mean_CIc_male) <- c("SITE", "mean_CIc_male")

summary_mean_CIc_male <- data.frame(
  mean_mean_CIc_male = mean(Mean_CIc_male$mean_CIc_male),
  max_mean_CIc_male = max(Mean_CIc_male$mean_CIc_male),
  min_mean_CIc_male = min(Mean_CIc_male$mean_CIc_male),
  sd_mean_CIc_male = sd(Mean_CIc_male$mean_CIc_male)
)

#### SD_CIc 
SD_CIc_male <- aggregate(Legset$ConventionalCI[Legset$Sex == 1], by = list(Legset$SITE[Legset$Sex == 1]), FUN = sd)
colnames(SD_CIc_male) <- c("SITE", "sd_CIc_male")

summary_sd_CIc_male <- data.frame(
  mean_sd_CIc_male = mean(SD_CIc_male$sd_CIc_male, na.rm = TRUE),
  max_sd_CIc_male = max(SD_CIc_male$sd_CIc_male, na.rm = TRUE),
  min_sd_CIc_male = min(SD_CIc_male$sd_CIc_male, na.rm = TRUE),
  sd_sd_CIc_male = sd(SD_CIc_male$sd_CIc_male, na.rm = TRUE)
)

### Female
#### Mean_CIc
Mean_CIc_female <- aggregate(Legset$ConventionalCI[Legset$Sex == 2], by = list(Legset$SITE[Legset$Sex == 2]), FUN = mean)
colnames(Mean_CIc_female) <- c("SITE", "mean_CIc_female")

summary_mean_CIc_female <- data.frame(
  mean_mean_CIc_female = mean(Mean_CIc_female$mean_CIc_female),
  max_mean_CIc_female = max(Mean_CIc_female$mean_CIc_female),
  min_mean_CIc_female = min(Mean_CIc_female$mean_CIc_female),
  sd_mean_CIc_female = sd(Mean_CIc_female$mean_CIc_female)
)

#### SD_CIc 
SD_CIc_female <- aggregate(Legset$ConventionalCI[Legset$Sex == 2], by = list(Legset$SITE[Legset$Sex == 2]), FUN = sd)
colnames(SD_CIc_female) <- c("SITE", "sd_CIc_female")

summary_sd_CIc_female <- data.frame(
  mean_sd_CIc_female = mean(SD_CIc_female$sd_CIc_female, na.rm = TRUE),
  max_sd_CIc_female = max(SD_CIc_female$sd_CIc_female, na.rm = TRUE),
  min_sd_CIc_female = min(SD_CIc_female$sd_CIc_female, na.rm = TRUE),
  sd_sd_CIc_female = sd(SD_CIc_female$sd_CIc_female, na.rm = TRUE)
)


# Print summary statistics
summary_mean_BIc_male
summary_mean_CIc_male
summary_sd_BIc_male
summary_sd_CIc_male
summary_mean_BIc_female
summary_mean_CIc_female
summary_sd_BIc_female
summary_sd_CIc_female
```

# 5. Compare the limb lengths and indices between males and females
## 5.1. Conduct t-tests on the limb lengths
```{r}
results_ttest_limblength <- data.frame()

# Conduct t-tests for limb lengths between males and females at each site
for (site in unique(Armset$SITE)) {
  male_hml <- subset(Armset, Sex == 1 & SITE == site)$finalHML
  female_hml <- subset(Armset, Sex == 2 & SITE == site)$finalHML
  male_rml <- subset(Armset, Sex == 1 & SITE == site)$finalRML
  female_rml <- subset(Armset, Sex == 2 & SITE == site)$finalRML

  male_fbl <- subset(Legset, Sex == 1 & SITE == site)$finalFBL
  female_fbl <- subset(Legset, Sex == 2 & SITE == site)$finalFBL
  male_tml <- subset(Legset, Sex == 1 & SITE == site)$finalTML
  female_tml <- subset(Legset, Sex == 2 & SITE == site)$finalTML

  if (length(male_hml) >= 3 & length(female_hml) >= 3 & length(male_rml) >= 3 & length(female_rml) >= 3 & length(male_fbl) >= 3 & length(female_fbl) >= 3 & length(male_tml) >= 3 & length(female_tml) >= 3) {
    ttest_hml <- t.test(male_hml, female_hml)
    ttest_rml <- t.test(male_rml, female_rml)
    ttest_fbl <- t.test(male_fbl, female_fbl)
    ttest_tml <- t.test(male_tml, female_tml)

    results_ttest_limblength <- rbind(results_ttest_limblength,
                                      data.frame(Site = site,
                                                 Variable = c("HML", "RML", "FBL", "TML"),
                                                 Group = rep("Male vs. Female", 4),
                                                 t_statistic = c(ttest_hml$statistic, ttest_rml$statistic, ttest_fbl$statistic, ttest_tml$statistic),
                                                 p_value = c(ttest_hml$p.value, ttest_rml$p.value, ttest_fbl$p.value, ttest_tml$p.value))
    )
  }
}

# HML
num_sig_ttests_HML <- sum(results_ttest_limblength$Variable == 'HML' & results_ttest_limblength$p_value < 0.05)
cat("Number of significant T-tests for HML:", num_sig_ttests_HML, "\n")

num_nonsig_ttests_HML <- sum(results_ttest_limblength$Variable == 'HML' & results_ttest_limblength$p_value >= 0.05)
cat("Number of non-significant T-tests for HML:", num_nonsig_ttests_HML, "\n")

# RML
num_sig_ttests_RML <- sum(results_ttest_limblength$Variable == 'RML' & results_ttest_limblength$p_value < 0.05)
cat("Number of significant T-tests for RML:", num_sig_ttests_RML, "\n")

num_nonsig_ttests_RML <- sum(results_ttest_limblength$Variable == 'RML' & results_ttest_limblength$p_value >= 0.05)
cat("Number of non-significant T-tests for RML:", num_nonsig_ttests_RML, "\n")

# FBL
num_sig_ttests_FBL <- sum(results_ttest_limblength$Variable == 'FBL' & results_ttest_limblength$p_value < 0.05)
cat("Number of significant T-tests for FBL:", num_sig_ttests_FBL, "\n")

num_nonsig_ttests_FBL <- sum(results_ttest_limblength$Variable == 'FBL' & results_ttest_limblength$p_value >= 0.05)
cat("Number of non-significant T-tests for FBL:", num_nonsig_ttests_FBL, "\n")

# TML
num_sig_ttests_TML <- sum(results_ttest_limblength$Variable == 'TML' & results_ttest_limblength$p_value < 0.05)
cat("Number of significant T-tests for TML:", num_sig_ttests_TML, "\n")

num_nonsig_ttests_TML <- sum(results_ttest_limblength$Variable == 'TML' & results_ttest_limblength$p_value >= 0.05)
cat("Number of non-significant T-tests for TML:", num_nonsig_ttests_TML, "\n")
```

## 5.2. Conduct t-tests on the indices
```{r}
results_ttest_BC <- data.frame()

# Conduct t-tests for BI and CI between males and females at each site
for (site in unique(Armset$SITE)) {
  male_bic <- subset(Armset, Sex == 1 & SITE == site)$ConventionalBI
  female_bic <- subset(Armset, Sex == 2 & SITE == site)$ConventionalBI
  male_cic <- subset(Legset, Sex == 1 & SITE == site)$ConventionalCI
  female_cic <- subset(Legset, Sex == 2 & SITE == site)$ConventionalCI

  if (length(male_bic) >= 3 & length(female_bic) >= 3 & length(male_cic) >= 3 & length(female_cic) >= 3) {
    ttest_bic <- t.test(male_bic, female_bic)
    ttest_cic <- t.test(male_cic, female_cic)

    results_ttest_BC <- rbind(results_ttest_BC,
                              data.frame(Site = site,
                                         Variable = c("BIc", "CIc"),
                                         Group = rep("Male vs. Female", 2),
                                         t_statistic = c(ttest_bic$statistic, ttest_cic$statistic),
                                         p_value = c(ttest_bic$p.value, ttest_cic$p.value))
    )
  }
}

# Count the number of significant and non-significant t-tests
num_sig_ttests_BIc <- sum(results_ttest_BC$Variable == 'BIc' & results_ttest_BC$p_value < 0.05)
cat("Number of significant T-tests for BIc:", num_sig_ttests_BIc, "\n")

num_nonsig_ttests_BIc <- sum(results_ttest_BC$Variable == 'BIc' & results_ttest_BC$p_value >= 0.05)
cat("Number of non-significant T-tests for BIc:", num_nonsig_ttests_BIc, "\n")

num_sig_ttests_CIc <- sum(results_ttest_BC$Variable == 'CIc' & results_ttest_BC$p_value < 0.05)
cat("Number of significant T-tests for CIc:", num_sig_ttests_CIc, "\n")

num_nonsig_ttests_CIc <- sum(results_ttest_BC$Variable == 'CIc' & results_ttest_BC$p_value >= 0.05)
cat("Number of non-significant T-tests for CIc:", num_nonsig_ttests_CIc, "\n")
```
